### 2020-07-25 paper/sections/introduction.tex
Initial commit

\section{Introduction}
\label{Section: introduction}

### 2020-07-25 paper/sections/relatedwork.tex
Initial commit

\section{Related Works}
\label{Section: related_works}

### 2020-08-05 paper/sections/introduction.tex
update introduction

@@
 \label{Section: introduction}
+With the increasing demand for continuous video analysis in public safety and transportation, more and more cameras are being deployed to various locations.
+Video analysis can be completed according to the video analysis application built by different models, which can free the staff from complex and boring tasks or search through massive amounts of video data to find what you're looking for quickly.
+In recent years, we have also witnessed the emergence of a large number of excellent models for target detection.
+\cite{jiang2018chameleon}
+
+For the collected video, the classical computer vision and deep neural network technology are generally used for video analysis.
+Video analysis applications consist of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector.
+Such an application always having multiple "knobs", such as frame rate, resolution, and model (for example, MobileNet, ResNet, or InceptionResNet), for different combinations of values of knobs is called different configurations.
+Since video analysis is a very complex process, we pay much attention to the consumption of resources in the calculation process, and the accuracy of inference is also our focus.
+Therefore, the problem that follows is how to balance the consumption of resources and accuracy.
+Choosing different configurations will affect the resource consumption and accuracy caused by video analysis.
+For example, using a complex model and high resolution can obviously accurately detect the target object, but it also requires more computing resources.
+However, choosing a simple model and low resolution can significantly reduce resource consumption, although it reduces the accuracy to some extent.
+And in the case of a highway video analysis, due to the rate of car travel cannot be predicted in advance, so when the car driving slowly(or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) without having to use a fixed on the whole video higher frame rate, this can significantly reduce resource consumption, but does not affect the accuracy of the video analysis.
+Our goal is to find a "best fit" configuration that takes up the minimum amount of computing resources and is accurate to the desired threshold.
+The most intuitive way to solve this problem is to find the best solution by exhaustive all configurations, but the number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs, so exhaustive configuration is a highly unrealistic approach.
+
+In this paper, we propose an approach based on reinforcement learning, which can skillfully use the temporal and spatial characteristics of video to select the "most appropriate" configuration, thus solving a difficult optimal configuration decision problem (reduced to linear time complexity) in a very low-cost way:
+
+\begin{itemize}
+\item Time related
+\item Spatial correlation
+\item Independent configuration
+\end{itemize}

### 2020-08-05 paper/sections/introduction.tex
update introduction

@@
 In recent years, we have also witnessed the emergence of a large number of excellent models for target detection.
-\cite{jiang2018chameleon}
 
@@
 And in the case of a highway video analysis, due to the rate of car travel cannot be predicted in advance, so when the car driving slowly(or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) without having to use a fixed on the whole video higher frame rate, this can significantly reduce resource consumption, but does not affect the accuracy of the video analysis.
-Our goal is to find a "best fit" configuration that takes up the minimum amount of computing resources and is accurate to the desired threshold.
+The best configuration for a video analytics pipeline alsovaries over time, often at a timescale of minutes or evenseconds\cite{jiang2018chameleon}, so our goal is to find a range of "best fit" configurations that takes up the minimum amount of computing resources and is accurate to the desired threshold.
 The most intuitive way to solve this problem is to find the best solution by exhaustive all configurations, but the number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs, so exhaustive configuration is a highly unrealistic approach.

### 2020-08-05 paper/sections/introduction.tex
update introduction

--- 2020-08-05 paper/sections/introduction.tex
@@
 In recent years, we have also witnessed the emergence of a large number of excellent models for target detection.
-\cite{jiang2018chameleon}
 
 For the collected video, the classical computer vision and deep neural network technology are generally used for video analysis.
-Video analysis applications consist of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector.
-Such an application always having multiple "knobs", such as frame rate, resolution, and model (for example, MobileNet, ResNet, or InceptionResNet), for different combinations of values of knobs is called different configurations.
+A video analysis application consists of a pipeline of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector.
+Such a pipeline always having multiple "knobs", such as frame rate, resolution, and model (for example, MobileNet, ResNet, or InceptionResNet), for different combinations of values of knobs are called different configurations.
 Since video analysis is a very complex process, we pay much attention to the consumption of resources in the calculation process, and the accuracy of inference is also our focus.
@@
 And in the case of a highway video analysis, due to the rate of car travel cannot be predicted in advance, so when the car driving slowly(or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) without having to use a fixed on the whole video higher frame rate, this can significantly reduce resource consumption, but does not affect the accuracy of the video analysis.
-Our goal is to find a "best fit" configuration that takes up the minimum amount of computing resources and is accurate to the desired threshold.
+The best configuration for a video analytics pipeline alsovaries over time, often at a timescale of minutes or even seconds\cite{jiang2018chameleon}, so our goal is to find a range of "best fit" configurations that takes up the minimum amount of computing resources and is accurate to the desired threshold.
 The most intuitive way to solve this problem is to find the best solution by exhaustive all configurations, but the number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs, so exhaustive configuration is a highly unrealistic approach.

### 2020-08-21 paper/sections/introduction.tex
related

--- 2020-08-05 paper/sections/introduction.tex
@@
 With the increasing demand for continuous video analysis in public safety and transportation, more and more cameras are being deployed to various locations.
-Video analysis can be completed according to the video analysis application built by different models, which can free the staff from complex and boring tasks or search through massive amounts of video data to find what you're looking for quickly.
+Video analysis can be completed according to the video analysis application built by different models \textcolor{note}{misunderstand of different models, tangchen amend}, which can free the staff from complex and boring tasks or search through massive amounts of video data to find what you're looking for quickly.
 In recent years, we have also witnessed the emergence of a large number of excellent models for target detection.
-\cite{jiang2018chameleon}
 
 For the collected video, the classical computer vision and deep neural network technology are generally used for video analysis.
-Video analysis applications consist of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector.
-Such an application always having multiple "knobs", such as frame rate, resolution, and model (for example, MobileNet, ResNet, or InceptionResNet), for different combinations of values of knobs is called different configurations.
+A video analysis application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector.
+Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., MobileNet, ResNet, or InceptionResNet).
+A combination of the knob values is a video analysis \emph{configuration}.
+The configuration space grows \emph{exponentially} with the number of knobs and their values.
 Since video analysis is a very complex process, we pay much attention to the consumption of resources in the calculation process, and the accuracy of inference is also our focus.
-Therefore, the problem that follows is how to balance the consumption of resources and accuracy.
+Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}.
+
 Choosing different configurations will affect the resource consumption and accuracy caused by video analysis.
@@
 However, choosing a simple model and low resolution can significantly reduce resource consumption, although it reduces the accuracy to some extent.
-And in the case of a highway video analysis, due to the rate of car travel cannot be predicted in advance, so when the car driving slowly(or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) without having to use a fixed on the whole video higher frame rate, this can significantly reduce resource consumption, but does not affect the accuracy of the video analysis.
-Our goal is to find a "best fit" configuration that takes up the minimum amount of computing resources and is accurate to the desired threshold.
-The most intuitive way to solve this problem is to find the best solution by exhaustive all configurations, but the number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs, so exhaustive configuration is a highly unrealistic approach.
+And in the case of a highway video analysis, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) without having to use a fixed on the whole video higher frame rate, this can significantly reduce resource consumption, but does not affect the accuracy of the video analysis.
 
-In this paper, we propose an approach based on reinforcement learning, which can skillfully use the temporal and spatial characteristics of video to select the "most appropriate" configuration, thus solving a difficult optimal configuration decision problem (reduced to linear time complexity) in a very low-cost way:
+The \emph{best} configuration for a video analytics pipeline also varies over time, often at a timescale of minutes or even seconds \cite{jiang2018chameleon}.
+Hence, our goal is to find a range of ``most appropriate'' configurations that takes up the minimum amount of computing resources and is accurate to the desired threshold.
+On the one hand, if one only profiles the processing pipeline to choose the best configuration \emph{once}, the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by picking a cheap configuration).
+On the other hand, if one periodically profiles the pipeline configurations to find an optimal resource-accuracy \emph{tradeoff} by exhaustive all configurations, it would be prohibitively expensive since the number of possible configurations is exponential in the number of knobs and their values, and thousands of configurations can be combined with just a few knobs.
+
+%The most intuitive way to solve this problem is to find the best solution by exhaustive all configurations, but the number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs, so exhaustive configuration is a highly unrealistic approach.
+
+For a video analytics application, choosing the ``most appropriate'' configuration is a complicated decision-making problem, which is challenging to be solved by rules.
+The reinforcement learning method is an excellent way to solve this unsupervised complex-environmental problem.
+In our solution, we tackle the following design challenges.
+
+%Also, one is not provided the well-labeled data on which configuration should be used in which time of the video, meaning this is an unsupervised learning task.
 
 \begin{itemize}	
-\item Time related
-\item Spatial correlation
-\item Independent configuration
+\item \emph{The best configuration for a video analytics pipeline changes over time with the environment.} The real-word environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second.
+As a dynamic video analysis configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contents, i.e., it can \emph{generate} video analysis configuration for video analysis in a different time.
+
+\item \emph{How to significantly reduce the resource cost of periodic configuration profiling.} The cost of periodically profiling often exceeds any resource savings gained by adapting the best configurations we end up selecting.
+We leverage a Reinforcement Learning-based agent to automatically pick the best configuration periodically, dramatically reducing the profiling cost.
+
+\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks.
+In practice, such a video analysis configuration is usually utilized in an online manner, and the solution has to learn from the video contents automatically.
 \end{itemize}
+
+To address the above challenges, we present a periodically configure approach based on reinforcement learning, called PerConfigure, which can dynamically select the ``most appropriate'' configuration according to intrusive dynamics of video contents, thus solving this difficult optimal configuration decision problem in a very low-cost way.
+The main contributions of this paper are summarized as follows.
+\textcolor{note}{zhaoliang add more contributions}
+
+\begin{itemize}
+
+\item We design an interactive training environment that can be applied to different online computer vision-based services.
+We propose an asynchronous advantage actor-critic-based \cite{mnih2016asynchronous} agent to evaluate and predict the performance of a video analysis configuration on video analysis.
+
+\item We build a reinforcement learning-based framework to train the agent in the above environment.
+The agent can learn to choose a ``most appropriate'' configuration for each timestamp of video analysis after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and resources.
+
+\item PerConfigure can achieve xx-xx\% higher accuracy with the
+same amount of resources, or achieve the same accuracy
+with only xx-xx\% of the resources.
+\end{itemize}
+
+%The rest of this paper is organized as follows.
+We discuss related works in Section \ref{Section: related_works}.
+We present our framework and detailed design in Section \ref{Section: design}.
+We present our solution's performance in Section \ref{Section: evaluation} and conclude the paper in Section \ref{Section: conclusion}.

### 2020-08-21 paper/sections/relatedwork.tex
related

@@
 \label{Section: related_works}
+
+\subsection{Static configuration optimization} 
+Several previous papers have considered optimizing video processing pipelines by either adjusting the configuration knobs or training specialized NN models.
+VideoStorm \cite{zhang2017videostorm} profiles thousands of video analytics queries on live video streams over large clusters, achieving resource-quality tradeoff with multi-dimensional configurations.
+VideoEdge \cite{hung2018videoedge} introduces \emph{dominant demand} to identify the best tradeoff between multiple resources and accuracy, and narrows the search space by identifying a ``Pareto ban'' of promising configurations.
+MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for
+deep stream processing under resource constraints.
+Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingest and video query.
+By tuning the share of computing resources of both phases, Focus achieves effective and flexible tradeoff of latency and accuracy of video analytics.
+These algorithms all profile and optimize video analytics only once at the beginning of the video.
+They do not handle changes in video stream content.
+But the optimal configurations do change over time because of the complex and changeable environment.
+
+\subsection{Dynamic configuration optimization}
+Some papers study how to dynamically optimize the configuration for video analytics when the video stream content changes.
+\cite{shen2017retrain_model} adaptively retrains the NN model to detect the set of popular objects as it changes over time in the video classification task.
+\cite{yang2019edge_coordinated} proposes an online video quality and computing resource configuration algorithm to gradually learn the optimal configuration strategy, effectively improving the analytic accuracy while providing the low-latency response.
+INFaaS \cite{romero2019infaas} automatically selects a model, hardware architecture, and any compiler optimizations, and makes scaling and resource allocation decisions when application load varies and the available resources vary over time.
+JCAB \cite{wang2020jcab} jointly optimizes
+configuration adaption and bandwidth allocation to address several critical challenges in edge-based video analytics systems,
+including edge capacity limitation, unknown network variation,
+intrusive dynamics of video contents. The online algorithm effectively balances analytics accuracy and energy
+consumption while keeping low system latency.
+
+The closest work to ours is Chameleon \cite{jiang2018chameleon}, which dynamically picks the best configurations for video analytics pipelines, reducing resource consumption
+with little degradation in accuracy.
+They leverage temporal and spatial correlation to amortizes the cost of profiling over time and across multiple cameras, and exploit the knob independence to reduce the search space from exponential to linear.
+Even the search space is linear, and the profiling cost is still expensive.
+Such a 24-hours video, Chameleon profiles the configuration space once in every profiling window (16s), it would profile 5400 times.
+One profiling cost grows linear in the number of configuration knobs and the number of values per knob.
+The total profiling cost which is equal to one profiling cost multiply the number of profiling (5400) is also significantly high.
+\textcolor{note}{a little strange, can tangchen help amend?} Our solution called PerConfigure leverages a reinforcement learning-agent to choose the best configuration periodically, significantly reducing the cost of profiling since the choosing time is extremely lower.

### 2020-09-04 paper/sections/introduction.tex
abstract
abstract,intro,related

@@
 \label{Section: introduction}
-With the increasing demand for continuous video analysis in public safety and transportation, more and more cameras are being deployed to various locations.
-Video analysis can be completed according to the video analysis application built by different models \textcolor{note}{misunderstand of different models, tangchen amend}, which can free the staff from complex and boring tasks or search through massive amounts of video data to find what you're looking for quickly.
-In recent years, we have also witnessed the emergence of a large number of excellent models for target detection.
+With the increasing demand for continuous video analytics in public safety and transportation, more and more cameras are being deployed to various locations.
+The video analytics are based on classical computer vision techniques as well as deep convolutional neural networks.
+In recent years, we have also witnessed the emergence of a large number of excellent models for target detection \cite{huang2017speed_accuracy}, such as FasterRCNN \cite{ren2015faster_rcnn}, RFCN \cite{dai2016r_fcn}, Multibox \cite{szegedy2014multibox}, SSD \cite{liu2016ssd} and YOLO \cite{redmon2016yolo}.
 
-For the collected video, the classical computer vision and deep neural network technology are generally used for video analysis.
-A video analysis application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector.
-Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., MobileNet, ResNet, or InceptionResNet).
-A combination of the knob values is a video analysis \emph{configuration}.
-The configuration space grows \emph{exponentially} with the number of knobs and their values.
-Since video analysis is a very complex process, we pay much attention to the consumption of resources in the calculation process, and the accuracy of inference is also our focus.
+For the collected video, the classical computer vision and deep neural network technology are generally used for video analytics.
+A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector.
+Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{howard2017mobilenets}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}).
+A combination of the knob values is a video analytics \emph{configuration}.
+The configuration space grows \emph{exponentially} with the number of knobs and their values \cite{jiang2018chameleon}.
+Since video analytics applications demand intensive computation resources and high accuracy, we pay much attention to the consumption of resources in the calculation process and the accuracy of inference.
 Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}.
 
-Choosing different configurations will affect the resource consumption and accuracy caused by video analysis.
+Apparently, choosing different configurations will affect resource consumption and accuracy.
 For example, using a complex model and high resolution can obviously accurately detect the target object, but it also requires more computing resources.
 However, choosing a simple model and low resolution can significantly reduce resource consumption, although it reduces the accuracy to some extent.
-And in the case of a highway video analysis, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) without having to use a fixed on the whole video higher frame rate, this can significantly reduce resource consumption, but does not affect the accuracy of the video analysis.
+And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) without having to use a fixed on the whole video higher frame rate, this can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.
 
@@
 On the one hand, if one only profiles the processing pipeline to choose the best configuration \emph{once}, the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by picking a cheap configuration).
-On the other hand, if one periodically profiles the pipeline configurations to find an optimal resource-accuracy \emph{tradeoff} by exhaustive all configurations, it would be prohibitively expensive since the number of possible configurations is exponential in the number of knobs and their values, and thousands of configurations can be combined with just a few knobs.
+On the other hand, if one periodically profiles the processing pipeline to find an optimal resource-accuracy \emph{tradeoff} by exhaustive all configurations, it would be prohibitively expensive since the configuration space is extremely large, and thousands of configurations can be combined with just a few knobs.
 
@@
 For a video analytics application, choosing the ``most appropriate'' configuration is a complicated decision-making problem, which is challenging to be solved by rules.
+An automatic approach is needed, one that is able to learn from video contents, to decide what is the best configuration for the current video content.
 The reinforcement learning method is an excellent way to solve this unsupervised complex-environmental problem.
@@
 \item \emph{The best configuration for a video analytics pipeline changes over time with the environment.} The real-word environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second.
-As a dynamic video analysis configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contents, i.e., it can \emph{generate} video analysis configuration for video analysis in a different time.
+As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contents, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
 
@@
 \item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks.
-In practice, such a video analysis configuration is usually utilized in an online manner, and the solution has to learn from the video contents automatically.
+In practice, such a video analytics configuration is usually utilized in an online manner, and the solution has to learn from the video contents automatically.
 \end{itemize}
 
-To address the above challenges, we present a periodically configure approach based on reinforcement learning, called PerConfigure, which can dynamically select the ``most appropriate'' configuration according to intrusive dynamics of video contents, thus solving this difficult optimal configuration decision problem in a very low-cost way.
+To address the above challenges, we present a content-driven automatic configuration framework based on reinforcement learning, called AutoConfigure, which can dynamically select the ``most appropriate'' configuration according to intrusive dynamics of video contents, thus solving this difficult optimal configuration decision problem in a very low-cost way.
 The main contributions of this paper are summarized as follows.
@@
 \begin{itemize}	
-
-\item We design an interactive training environment that can be applied to different online computer vision-based services.
-We propose an asynchronous advantage actor-critic-based \cite{mnih2016asynchronous} agent to evaluate and predict the performance of a video analysis configuration on video analysis.
+\item We design an interactive training environment that can be applied to different video analytics applications.
+We propose an asynchronous advantage actor-critic-based \cite{mnih2016asynchronous} agent to pick the best configuration for video analytics.
+Also, we define the elements of the RL-based approach, such as actions, states and rewards, to adapt the configuration to current video content.
 
 \item We build a reinforcement learning-based framework to train the agent in the above environment.
-The agent can learn to choose a ``most appropriate'' configuration for each timestamp of video analysis after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and resources.
+The agent can learn to choose a ``most appropriate'' configuration for each timestamp of video analytics after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and resources.
 
-\item PerConfigure can achieve xx-xx\% higher accuracy with the
+\item AutoConfigure can achieve xx-xx\% higher accuracy with the
 same amount of resources, or achieve the same accuracy
-with only xx-xx\% of the resources.
+with only xx-xx\% of the resources. Furthermore, AutoConfigure proves to be more efficient than existing baselines by creating an overhead of less than xx\% to the overall video analytics pipeline.
 \end{itemize}

### 2020-09-04 paper/sections/relatedwork.tex
abstract
abstract,intro,related

@@
 
+\subsection{Configuration optimization} 
 \subsection{Static configuration optimization}
-Several previous papers have considered optimizing video processing pipelines by either adjusting the configuration knobs or training specialized NN models.
+Several previous papers have considered optimizing video analytics pipelines by either adjusting the configuration knobs or training specialized NN models.
 VideoStorm \cite{zhang2017videostorm} profiles thousands of video analytics queries on live video streams over large clusters, achieving resource-quality tradeoff with multi-dimensional configurations.
 VideoEdge \cite{hung2018videoedge} introduces \emph{dominant demand} to identify the best tradeoff between multiple resources and accuracy, and narrows the search space by identifying a ``Pareto ban'' of promising configurations.
-MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for
-deep stream processing under resource constraints.
+MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints.
 Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingest and video query.
@@
 They do not handle changes in video stream content.
-But the optimal configurations do change over time because of the complex and changeable environment.
+But the optimal configurations do change over time because of the complex and changeable video stream contents.
 
@@
 INFaaS \cite{romero2019infaas} automatically selects a model, hardware architecture, and any compiler optimizations, and makes scaling and resource allocation decisions when application load varies and the available resources vary over time.
-JCAB \cite{wang2020jcab} jointly optimizes
-configuration adaption and bandwidth allocation to address several critical challenges in edge-based video analytics systems,
-including edge capacity limitation, unknown network variation,
-intrusive dynamics of video contents. The online algorithm effectively balances analytics accuracy and energy
-consumption while keeping low system latency.
+QuickAdapt \cite{ullah2019quickadapt} uses
+descriptive statistics of security events data and fuzzy rules to
+enable a Big Data Cyber Security Analytics (BDCA) system to quickly adapt to the changes in security events data.
+JCAB \cite{wang2020jcab} jointly optimizes configuration adaption and bandwidth allocation to address several critical challenges in edge-based video analytics systems, including edge capacity limitation, unknown network variation, intrusive dynamics of video contents.
+The online algorithm effectively balances analytics accuracy and energy consumption while keeping low system latency.
+\cite{argerich2019orchestration} leverages tabular Q-learning to adapt configuration, but their agent's states only consider last latency.
+Our framework pays attention to the complex and changeable video stream contents, and picks the best configuration according to current video content.
 
-The closest work to ours is Chameleon \cite{jiang2018chameleon}, which dynamically picks the best configurations for video analytics pipelines, reducing resource consumption
-with little degradation in accuracy.
-They leverage temporal and spatial correlation to amortizes the cost of profiling over time and across multiple cameras, and exploit the knob independence to reduce the search space from exponential to linear.
+The closest work to ours is Chameleon \cite{jiang2018chameleon}, which dynamically picks the best configurations for video analytics pipelines, reducing resource consumption with little degradation in accuracy.
+They leverage temporal and spatial correlation to amortizes the cost of profiling over time and across multiple cameras, and exploit the knob independence to reduce the search space from exponential to linear.\cite{jiang2018chameleon} Notice that Chameleon still has non-trivial room for improvement compared to the optimal (idealized) performance, i.e.,
+periodic updating with zero profiling cost.
 Even the search space is linear, and the profiling cost is still expensive.
@@
 One profiling cost grows linear in the number of configuration knobs and the number of values per knob.
-The total profiling cost which is equal to one profiling cost multiply the number of profiling (5400) is also significantly high.
-\textcolor{note}{a little strange, can tangchen help amend?} Our solution called PerConfigure leverages a reinforcement learning-agent to choose the best configuration periodically, significantly reducing the cost of profiling since the choosing time is extremely lower.
+The total profiling cost is also significantly high, which is equal to one profiling cost multiply the number of profiling (5400).
+Our solution, called AutoConfigure, leverages a reinforcement learning-agent to automatically choose the best configuration periodically, significantly reducing the cost of profiling since the agent's choosing time is extremely lower.

### 2020-09-08 paper/sections/introduction.tex
minor ab and intro

@@
 Apparently, choosing different configurations will affect resource consumption and accuracy.
-For example, using a complex model and high resolution can obviously accurately detect the target object, but it also requires more computing resources.
-However, choosing a simple model and low resolution can significantly reduce resource consumption, although it reduces the accuracy to some extent.
-And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) without having to use a fixed on the whole video higher frame rate, this can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.
+For example, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources.
+However, choosing a simple model with low resolution can significantly reduce resource consumption, although it reduces the accuracy to some extent.
+Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy.
+And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout whole video.
+This can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.
 
@@
 \begin{itemize}	
-\item \emph{The best configuration for a video analytics pipeline changes over time with the environment.} The real-word environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second.
+\item \emph{The best configuration for a video analytics pipeline changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second.
 As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contents, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.

### 2020-09-26 paper/sections/introduction.tex
add some figures

@@
 Apparently, choosing different configurations will affect resource consumption and accuracy.
-For example, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources.
-However, choosing a simple model with low resolution can significantly reduce resource consumption, although it reduces the accuracy to some extent.
+As shown in~\autoref{fig1}, at a fixed frame rate, using a complex model with high resolution(such as FasterRCNN+InceptionResnet 1024p) can obviously and accurately detect the target object, but it also requires more computing resources.
+However, when using the same model, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy.
+Another example is that choosing a simple model with low resolution(such as FasterRCNN+ResNet50 640p) can significantly reduce resource consumption, although it reduces the accuracy to some extent.
 Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy.
@@
 This can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.
+We use~\autoref{fig2} to support that, the data in this figure come from a real road.
+It can be found that with the decrease of frame rate, the resource consumption can be significantly reduced, but the decrease of accuracy is partly acceptable.
+
+\begin{figure}[h]
+\includegraphics[width=9cm,height=5cm]{figures/figure1.jpg}
+\centering
+\caption{The effect of different models and resolutions on accuracy and processing time at a fixed frame rate.}
+\label{fig1}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=9cm,height=5cm]{figures/figure2.jpg}
+\centering
+\caption{Under the best model, the accuracy and processing time vary with the different frame rate.}
+\label{fig2}
+\end{figure}
 

### 2020-09-28 paper/sections/introduction.tex
update

@@
 Apparently, choosing different configurations will affect resource consumption and accuracy.
-As shown in~\autoref{fig1}, at a fixed frame rate, using a complex model with high resolution(such as FasterRCNN+InceptionResnet 1024p) can obviously and accurately detect the target object, but it also requires more computing resources.
+As shown in~\autoref{fig1}, at a fixed frame rate, using a complex model with high resolution (such as FasterRCNN+InceptionResnet 1024p) can obviously and accurately detect the target object, but it also requires more computing resources.
 However, when using the same model, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy.
-Another example is that choosing a simple model with low resolution(such as FasterRCNN+ResNet50 640p) can significantly reduce resource consumption, although it reduces the accuracy to some extent.
+Another example is that choosing a simple model with low resolution (such as FasterRCNN+ResNet50 640p) can significantly reduce resource consumption, although it reduces the accuracy to some extent.
 Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy.
@@
 \begin{figure}[h]
-\includegraphics[width=9cm,height=5cm]{figures/figure1.jpg}
+\includegraphics[width=9cm,height=5cm]{figures/figure1.pdf}
 \centering
@@
 \begin{figure}[h]
-\includegraphics[width=9cm,height=5cm]{figures/figure2.jpg}
+\includegraphics[width=9cm,height=5cm]{figures/figure2.pdf}
 \centering

### 2020-11-13 paper/sections/experiment.tex
ICME

\section{Experiment}
\label{Section: experiment}

\subsection{Experiment Setup}

\subsection{some results}

\begin{table}[!t]
%\begin{table}[H]
	\centering
	%     \begin{tabular}{lll}
	\resizebox{0.5\textwidth}{!}{
		\begin{tabular}{lcc}
			\toprule
			Model and Image size & Inference time & Accuracy  \\ \midrule
			SSD MobileNetV2 320p          & 49.5 ms  &  xxx            \\
			SSD MobileNetV2 640p          & 58.5 ms  &  0.494            \\
			SSD ResNet152V1 640p          & 100 ms  &  0.579            \\
			SSD ResNet152V1 1024p          & 182.3 ms  &  0.614            \\
			FasterRCNN ResNet50V1 640p          & 106.4 ms  &  0.637            \\
			FasterRCNN ResNet50V1 1024p          & 120.5 ms  &  0.786           \\
			FasterRCNN InceptionResNetV2 640p          & 361.8 ms  &  0.734            \\
			FasterRCNN InceptionResNetV2 1024p          & 418.4 ms  &  1            \\
			\bottomrule
	\end{tabular}}
	\caption{Inference time and F1 for different models and resolutions car truck}
	\label{tab: latency-overhead}
	% \vspace{-0.5cm}
\end{table}

\begin{table}[!t]
	%\begin{table}[H]
	\centering
	%     \begin{tabular}{lll}
	\resizebox{0.5\textwidth}{!}{
		\begin{tabular}{lcc}
			\toprule
			Model and Image size & Inference time & Accuracy  \\ \midrule
			SSD MobileNetV2 320p          & 49.5 ms  &  xxx            \\
			SSD MobileNetV2 640p          & 58.5 ms  &  0.753            \\
			SSD ResNet152V1 640p          & 100 ms  &  0.886            \\
			SSD ResNet152V1 1024p          & 182.3 ms  &  0.942            \\
			FasterRCNN ResNet50V1 640p          & 106.4 ms  &  0.889            \\
			FasterRCNN ResNet50V1 1024p          & 120.5 ms  &  0.98           \\
			FasterRCNN InceptionResNetV2 640p          & 361.8 ms  &  0.965            \\
			FasterRCNN InceptionResNetV2 1024p          & 418.4 ms  &  1            \\
			\bottomrule
	\end{tabular}}
	\caption{Inference time and F1 for different models and resolutions}
	\label{tab: latency-overhead}
	% \vspace{-0.5cm}
\end{table}

### 2020-11-13 paper/sections/experiment.tex
add datasets info

@@
 \subsection{Experiment Setup}
-
-\subsection{some results}
+\textbf{Datasets:} Due to most of public sources datasets cannot fully satisfy all configuration choices, for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution, while others can guarantee resolution but cannot provide sufficient frame rate, but in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to use Youtube video as fellows.
+First, in order to eliminate the bias caused by Cookies and personal preferences, we use private browsing mode to search keywords (e.g., "drivecam highway hd").
+Second, manually delete irrelevant videos (e.g., ads for some driving recorders) and download videos that are longer than ten minutes(and keep only the first 10 minutes).
+In addition, these videos need to be as dynamic as the real world, such as not standing still for too long.
+Becaues of none of these videos contained ground truth, we used the data of the original video output from DNN as the tags to calculate the accuracy.
+For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 30$\%$ confidence score \textcolor{note}{this may need to be modified, chen tang}.
+\subsection{Some results}
 

### 2020-11-14 paper/sections/experiment.tex
figure results

@@
 First, in order to eliminate the bias caused by Cookies and personal preferences, we use private browsing mode to search keywords (e.g., "drivecam highway hd").
-Second, manually delete irrelevant videos (e.g., ads for some driving recorders) and download videos that are longer than ten minutes(and keep only the first 10 minutes).
+Second, manually delete irrelevant videos (e.g., ads for some driving recorders) and download videos that are longer than ten minutes.
 In addition, these videos need to be as dynamic as the real world, such as not standing still for too long.
 Becaues of none of these videos contained ground truth, we used the data of the original video output from DNN as the tags to calculate the accuracy.
-For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 30$\%$ confidence score \textcolor{note}{this may need to be modified, chen tang}.
+For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 50$\%$ confidence score \textcolor{note}{this may need to be modified, chen tang}.
 \subsection{Some results}
 
-\begin{table}[!t]
-%\begin{table}[H]
-	\centering
-	%     \begin{tabular}{lll}
-	\resizebox{0.5\textwidth}{!}{
-		\begin{tabular}{lcc}
-			\toprule
-			Model and Image size & Inference time & Accuracy  \\ \midrule
-			SSD MobileNetV2 320p          & 49.5 ms  &  xxx            \\
-			SSD MobileNetV2 640p          & 58.5 ms  &  0.494            \\
-			SSD ResNet152V1 640p          & 100 ms  &  0.579            \\
-			SSD ResNet152V1 1024p          & 182.3 ms  &  0.614            \\
-			FasterRCNN ResNet50V1 640p          & 106.4 ms  &  0.637            \\
-			FasterRCNN ResNet50V1 1024p          & 120.5 ms  &  0.786           \\
-			FasterRCNN InceptionResNetV2 640p          & 361.8 ms  &  0.734            \\
-			FasterRCNN InceptionResNetV2 1024p          & 418.4 ms  &  1            \\
-			\bottomrule
-	\end{tabular}}
-	\caption{Inference time and F1 for different models and resolutions car truck}
-	\label{tab: latency-overhead}
-	% \vspace{-0.5cm}
-\end{table}
+%\begin{table}[!t]
+%%\begin{table}[H]
+%	\centering
+%	%     \begin{tabular}{lll}
+%	\resizebox{0.5\textwidth}{!}{
+%		\begin{tabular}{lcc}
+%			\toprule
+%			Model and Image size & Inference time & Accuracy  \\ \midrule
+%			SSD MobileNetV2 320p          & 49.5 ms  &  xxx            \\
+%			SSD MobileNetV2 640p          & 58.5 ms  &  0.494            \\
+%			SSD ResNet152V1 640p          & 100 ms  &  0.579            \\
+%			SSD ResNet152V1 1024p          & 182.3 ms  &  0.614            \\
+%			FasterRCNN ResNet50V1 640p          & 106.4 ms  &  0.637            \\
+%			FasterRCNN ResNet50V1 1024p          & 120.5 ms  &  0.786           \\
+%			FasterRCNN InceptionResNetV2 640p          & 361.8 ms  &  0.734            \\
+%			FasterRCNN InceptionResNetV2 1024p          & 418.4 ms  &  1            \\
+%			\bottomrule
+%	\end{tabular}}
+%	\caption{Inference time and F1 for different models and resolutions car truck}
+%	\label{tab: latency-overhead}
+%	% \vspace{-0.5cm}
+%\end{table}
+%
+%\begin{table}[!t]
+%	%\begin{table}[H]
+%	\centering
+%	%     \begin{tabular}{lll}
+%	\resizebox{0.5\textwidth}{!}{
+%		\begin{tabular}{lcc}
+%			\toprule
+%			Model and Image size & Inference time & Accuracy  \\ \midrule
+%			SSD MobileNetV2 320p          & 49.5 ms  &  xxx            \\
+%			SSD MobileNetV2 640p          & 58.5 ms  &  0.753            \\
+%			SSD ResNet152V1 640p          & 100 ms  &  0.886            \\
+%			SSD ResNet152V1 1024p          & 182.3 ms  &  0.942            \\
+%			FasterRCNN ResNet50V1 640p          & 106.4 ms  &  0.889            \\
+%			FasterRCNN ResNet50V1 1024p          & 120.5 ms  &  0.98           \\
+%			FasterRCNN InceptionResNetV2 640p          & 361.8 ms  &  0.965            \\
+%			FasterRCNN InceptionResNetV2 1024p          & 418.4 ms  &  1            \\
+%			\bottomrule
+%	\end{tabular}}
+%	\caption{Inference time and F1 for different models and resolutions}
+%	\label{tab: latency-overhead}
+%	% \vspace{-0.5cm}
+%\end{table}
 
-\begin{table}[!t]
-	%\begin{table}[H]
-	\centering
-	%     \begin{tabular}{lll}
-	\resizebox{0.5\textwidth}{!}{
-		\begin{tabular}{lcc}
-			\toprule
-			Model and Image size & Inference time & Accuracy  \\ \midrule
-			SSD MobileNetV2 320p          & 49.5 ms  &  xxx            \\
-			SSD MobileNetV2 640p          & 58.5 ms  &  0.753            \\
-			SSD ResNet152V1 640p          & 100 ms  &  0.886            \\
-			SSD ResNet152V1 1024p          & 182.3 ms  &  0.942            \\
-			FasterRCNN ResNet50V1 640p          & 106.4 ms  &  0.889            \\
-			FasterRCNN ResNet50V1 1024p          & 120.5 ms  &  0.98           \\
-			FasterRCNN InceptionResNetV2 640p          & 361.8 ms  &  0.965            \\
-			FasterRCNN InceptionResNetV2 1024p          & 418.4 ms  &  1            \\
-			\bottomrule
-	\end{tabular}}
-	\caption{Inference time and F1 for different models and resolutions}
-	\label{tab: latency-overhead}
-	% \vspace{-0.5cm}
-\end{table}
+%\begin{figure}[!t]
+%	\includegraphics[width=9cm,height=8cm]{figures/m6.pdf}
+%	\centering
+%	\caption{The effect of different models, frame rate, and resolutions on accuracy and processing time.
+AutoConfigure (blue) consistently outperforms the baseline of one-time update (magenta) across different datasets.
+Each dot represents the results of running each solution.}
+%	\label{fig_m6}
+%\end{figure}
+
+\begin{figure*}[!t]
+		\begin{minipage}[t]{0.32\linewidth}
+			\centerline{\includegraphics[width=6.5cm]{figures/m6.pdf}}
+			\centerline{(a) M6}
+		\end{minipage}
+		\hfill
+		\begin{minipage}[t]{0.32\linewidth}
+			\centerline{\includegraphics[width=6.5cm]{figures/duke.pdf}}
+			\centerline{(b) Duke}
+		\end{minipage}
+		\hfill
+		\begin{minipage}[t]{0.32\linewidth}
+			\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
+			\centerline{(c) Multi Camera Dataset}
+		\end{minipage}		
+		\caption{The effect of different models, frame rate, and resolutions on accuracy and processing time.
+AutoConfigure (blue) consistently outperforms the baseline of one-time update (magenta) across different datasets.
+Each dot represents the results of running each solution.}
+		\label{fig_results}
+\end{figure*}

### 2020-11-14 paper/sections/experiment.tex
update datasets info

@@
 For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 50$\%$ confidence score \textcolor{note}{this may need to be modified, chen tang}.
+
+Based on the above filtering strategy, we finally selected three datasets:
+
+M6: The M6 is the longest motorway in Britain and the most important road from the Midlands to the West Coast.
+Thousands of cars travel on it every day.
+This video was taken from a traffic camera, and its natural dynamics allows us to experiment with this video.
+
+Duke: Duke is a video from a fixed camera placed at an intersection.
+Because it is fixed in the middle of the intersection, the traffic flow in the video increases or decreases periodically as the traffic light change.
+
+Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.
 \subsection{Some results}

### 2020-11-18 paper/sections/experiment.tex
Add selection and parameters

@@
 Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.
+\subsection{Configure Selection}
+We simulate the environment with three object detection models, which are SSD ResNet152V1, FasterRCNN ResNet50V1, FasterRCNN InceptionResNetV2.
+For each model, two kinds of image resolution for inference, which is $1024\times1024$ and $640\times640$, can be picked up.
+Besides choosing a proper configure of model and image resolution, AutoConfigure needs to select a proper number of frames per second(fps).
+We in our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}.
+Therefore, the number of actions that the agent can choose is forty-eight.
+\subsection{Experiment Parameters}
+We apply deep Q-learning policy to train the agent.
+In the training procedure, we build up eight independently identical environments for each data set to speed up the training and decrease the dependency of the data.
+The leaning rate is set to 0.001.
+The discount factor is set to 0.9.
+For each dataset, we train the agent 10 epochs and 1000 steps per epoch.
+The exploration factor is 0.9.
 \subsection{Some results}

### 2020-11-26 paper/sections/design.tex
design

\section{Detailed Design}
\label{Section: design}

\begin{figure*}[!t]
	\centerline{\includegraphics[width=0.9\linewidth]{figures/DQN.jpg}}
	%	\vspace{0.2cm}
	\caption{Applying reinforcement learning to automatic configuration.\textcolor{note}{redo}}
	\label{fig: DQN}
\end{figure*}

Figure~\ref{fig: DQN} summarizes how RL can be applied to automatic configuration. Briefly, it is a reinforcement learning-based system to train an agent to choose a proper configuration $ c $ for one video chunk to be inferenced. We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback in the following subsections. We provide experimental details of all the hyperparameters in Section~\ref{Section: experiment}. %% \\

\subsection{Problem Formulation}
\label{subsec: formulation}

Without loss of generality, we denote the object detection service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input video chunk $ x_i $. It has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each input video chunk $ x \in X_{\rm ref} $ using \emph{reference configuration} (the most expensive configuration). We use this $ \vec{y}_{\rm ref} $ as the ground truth label. For each video chunk $ x_c $ that uses a configuration $ c $, the output $ \vec{y}_c = M(x_c) $. Therefore, we have an accuracy metric $ \mathcal{A}_c $ by comparing $ \vec{y}_{\rm ref} $ and $ \vec{y}_c $. In general, we use the F1 score as the accuracy $ \mathcal{A} $, which is the harmonic mean of precision and recall, consistent with prior work~\cite{jiang2018chameleon,kang2017f1_noscope,zhang2017f1_live}. Besides, to compute the accuracy of a frame that was not sampled by $ c $, we use the location of objects from the previous sampled frame.

For the cost of the object detection service, we use average GPU processing time per frame as the metric of resource consumption, because GPU is the dominant resource for the majority of video processing workloads. We also denote the metric of resource consumption as $ \hat{s}_{ic} $ that for an input video chunk $ x_i $ and a given configuration $ c $. For a reference configuration $ c_{\rm ref} $, the reference resource consumption is $ \hat{s}_{\rm ref} $.

Initially, the agent tries different configurations $ c $ to obtain inference results image $ x_c $ from input video chunk $ x $. To obtain object detection results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, the agent uses the choosen configuration $ c $ and the reference configuration $ x_{\rm ref} $. Comparing the two object detection results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $ and two resource consumptions $ \{\hat{s}_{\rm ref}, \hat{s}_c\} $, the agent computes the resource consumption ratio $ \Delta s = \frac{\hat{s}_c}{\hat{s}_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $.

\subsection{RL Agent Design}

The RL agent is expected to give a proper configuration $ c $ for minimizing the resource consumption $ \hat{s}_c $ while keeping the accuracy $ \mathcal{A} $. For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $. Therefore we can use the Deep Q-learning Network \cite{DQN} as the RL agent. But the naive Deep Q-learning Network can not work well in this task, because the state space of reinforcement learning is too large if we directly treat video chunk as the input. To preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge.  
%because of the following challenges: %% \\
%
%\begin{itemize}
%	\item The state space of reinforcement learning is too large. To preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge. 
%	\item It takes a long time to train one step in a large inference neural network, making the training process too time-consuming.
%	\item The RL agent starts training from random trials and learns afterward from the reward feedback. When training from a randomly initialized neural network, the reward feedback is very sparse, making it difficult for the agent to learn.
%\end{itemize}

To address this challenges, we extract the top $k_1$ representative images from each chunk as spatial correlations of video chunk. We use a pre-trained small neural network to extract the structural information embeddings $ \{e_1,e_2,...,e_{k_1}\} $ of the images to reduce the input dimension and accelerate the training procedure. This is a commonly used strategy in training a deep neural network~\cite{finetunning,finetunning2}. In this work, we use the early convolution layers of MobileNetV2~\cite{MobileNetV2} as the image feature extractor $ \mathcal{E}(\cdot) $ for its efficiency in image classification. To extract the temporal correlations of video chunk, we obtain $ \{\hat{e}_1,\hat{e}_2,...,\hat{e}_{{k_1}-1}\} $ by each embedding subtracting previous embedding. Besides, we record the last $k_2$ configurations $ \{c_1,c_2,...,c_{k_2}\} $. To Solve that vectors of different lengths are not conducive to input to the neural network, we use fully connected layer to transform the spatial embedding $ \{e_1,e_2,...,e_{k_1}\} $, temporal embedding $ \{\hat{e}_1,\hat{e}_2,...,\hat{e}_{{k_1}-1}\} $, and recent configuration $ \{c_1,c_2,...,c_{k_2}\} $ to the fixed length vector, similar to the work~\cite{pensieve}. We formulate the fixed length vector $ s $ as \emph{states} and the configuration $ c $ as discrete \emph{actions}.

\subsection{Reinforcement Learning-based Framework}

In our system, we define 48 discrete actions to indicate 48 configuration, and the specific configurations are provided in Section~\ref{Section: experiment}. We denote the \emph{action-value function} as $ Q(s, c; \theta) $ and the optimal compression quality level at time $ t $ as $  c_t = {\rm argmax}_cQ(s, c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $. In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $. Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over state  $ s $ and the configuration $ c $~\cite{DQN}. When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.

In the training phase, the RL agent firstly using an $\epsilon-$greedy method to take some random trials to observe the environment's reaction and decreases the randomness when training afterward. In iteration $t$, we input state $s_t $ to neural network $ \phi $. The RL agent $\phi$ generates a specific configuration $c_t$. The framework processes the video chunk $x_t$ using configuration $c_t$ to inference object detection services and obtains reward $r_t$. Then the framework obtains the next video chunk $x_{t+1}$ and generates the next state $ s_{t+1} $. The framework stores transition $(s_t, c_t, r_t, s_{t+1})$ in a memory buffer $\mathcal{D}$. Especially, the transition $(s_t, c_t, r_t, s_{t+1} )$ is uesd to compute the loss function. All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $. The training procedure would converge when the agent's randomness keeps decaying. Finally, the agent's action is based on its historical ``optimal'' experiences. The training procedure is presented in Algorithm~\ref{alg: rl-train}.

\begin{algorithm}[!t]
		\caption{Training RL agent $ \phi $} %in environment $ \{\mathcal{X}, M\} $}
		\label{alg: rl-train}
		\begin{algorithmic}[1]	
			\STATE Initialize action-value function $ Q $ with random weights $ \theta $, replay memory buffer $ \mathcal{D} $ and state $ s_1 $				
			\FOR {$t \in 1,2,\cdots, K$}
			\STATE \textbf{1) Exploration}
			\STATE With probability $\epsilon$:
			\STATE \hspace{1em} $c_t \leftarrow$ a random valid value 
			\STATE Otherwise:
			\STATE \hspace{1em} $ c_t \leftarrow {\rm argmax}_cQ(s_t, c; \theta) $

			\STATE \textbf{2) Reward calcuation} 
			\STATE Process video chunk $ x_t $ using configuration $ c_t $ to inference
			\STATE Obtain $ (\vec{y}_{\rm ref}, \vec{y}_c) $ from the object detection service
			\STATE Compute reward $ r \leftarrow R(\Delta s, \mathcal{A}_c) $ according to \ref{subsec: reward} Reward Feedback Design 
			\STATE \textbf{3) Gradient descent}
			\STATE Obtain next video chunk $ x_{t+1} $
			\STATE Generate next state $ s_{t+1} $
			\STATE $ \mathcal{D} \leftarrow \mathcal{D} \bigcup \{(s_t, c_t, r_t, s_{t+1} \} $
			\STATE Sample a randomly mini-batch of transitions $ (s_j, c_j, r_j, s_{j+1}) $ from memory buffer $ \mathcal{D} $
			\STATE $ y_j \leftarrow r_j + \gamma \max_{c'}Q(s_{j+1}, c'; \theta) $
			\STATE Perform a gradient descent step on $ \big(y_j - Q(s_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
			\ENDFOR
		\end{algorithmic}
\end{algorithm}

\subsection{Reward Feedback Design}
\label{subsec: reward}

In our solution, the agent is trained by the reward feedback. In the above formulation, we define resource consumption rate $ \Delta s = \frac{\hat{s}_c}{\hat{s}_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ at configuration $ c $. Basically, we want the agent to choose a proper configuration for minimizing the resource consumption while remaining acceptable accuracy. Therefore the overall reward $ r $ should be positively correlated with the accuracy $ \mathcal{A} $ while negatively with the resource consumption ratio $ \Delta s $. We introduce a linear factor $ \beta $ to form a linear combination $ r = \beta \mathcal{A} - (1-\beta) \Delta s  $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $. %% \\

### 2020-11-26 paper/sections/experiment.tex
design

@@
 
-\subsection{Experiment Setup}
-\textbf{Datasets:} Due to most of public sources datasets cannot fully satisfy all configuration choices, for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution, while others can guarantee resolution but cannot provide sufficient frame rate, but in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to use Youtube video as fellows.
+\subsection{Datasets}
+\textcolor{note}{this section is too long}
+
+Due to most of public sources datasets cannot fully satisfy all configuration choices, for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution, while others can guarantee resolution but cannot provide sufficient frame rate, but in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to use Youtube video as fellows.
 First, in order to eliminate the bias caused by Cookies and personal preferences, we use private browsing mode to search keywords (e.g., "drivecam highway hd").
@@
 Becaues of none of these videos contained ground truth, we used the data of the original video output from DNN as the tags to calculate the accuracy.
-For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 50$\%$ confidence score \textcolor{note}{this may need to be modified, chen tang}.
-
-Based on the above filtering strategy, we finally selected three datasets:
+For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 50$\%$ confidence score.Based on the above filtering strategy, we finally selected three datasets:
 
@@
 Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.
+
+\begin{figure*}[!t]
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/m6.pdf}}
+		\centerline{(a) M6}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/duke.pdf}}
+		\centerline{(b) Duke}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
+		\centerline{(c) Multi Camera Dataset}
+	\end{minipage}		
+	\caption{The effect of different models, frame rate, and resolutions on accuracy and processing time.
+AutoConfigure (blue) consistently outperforms the baseline of one-time update (magenta) across different datasets.
+Each dot represents the results of running each solution.}
+	\label{fig_results}
+\end{figure*}
+
 \subsection{Configure Selection}
@@
 The exploration factor is 0.9.
-\subsection{Some results}
+The inference models are implemented in Tensorflow and are pretrained on standard image datasets \cite{trade-offs}, and the switching of video frame rate and resolution is done by FFmpeg \cite{ffmpeg}.
+\subsection{Experiment Results}
 
@@
 %\end{figure}
-
-\begin{figure*}[!t]
-		\begin{minipage}[t]{0.32\linewidth}
-			\centerline{\includegraphics[width=6.5cm]{figures/m6.pdf}}
-			\centerline{(a) M6}
-		\end{minipage}
-		\hfill
-		\begin{minipage}[t]{0.32\linewidth}
-			\centerline{\includegraphics[width=6.5cm]{figures/duke.pdf}}
-			\centerline{(b) Duke}
-		\end{minipage}
-		\hfill
-		\begin{minipage}[t]{0.32\linewidth}
-			\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
-			\centerline{(c) Multi Camera Dataset}
-		\end{minipage}		
-		\caption{The effect of different models, frame rate, and resolutions on accuracy and processing time.
-AutoConfigure (blue) consistently outperforms the baseline of one-time update (magenta) across different datasets.
-Each dot represents the results of running each solution.}
-		\label{fig_results}
-\end{figure*}

### 2020-11-26 paper/sections/introduction.tex
design

--- 2020-09-08 paper/sections/introduction.tex
@@
 \section{Introduction}
+\textcolor{note}{this section is too long}
+
 \label{Section: introduction}
@@
 The video analytics are based on classical computer vision techniques as well as deep convolutional neural networks.
-In recent years, we have also witnessed the emergence of a large number of excellent models for target detection \cite{huang2017speed_accuracy}, such as FasterRCNN \cite{ren2015faster_rcnn}, RFCN \cite{dai2016r_fcn}, Multibox \cite{szegedy2014multibox}, SSD \cite{liu2016ssd} and YOLO \cite{redmon2016yolo}.
+In recent years, we have also witnessed the emergence of a large number of excellent models for target detection \cite{trade-offs}, such as FasterRCNN \cite{ren2015faster_rcnn}, RFCN \cite{dai2016r_fcn}, Multibox \cite{szegedy2014multibox}, SSD \cite{liu2016ssd} and YOLO \cite{redmon2016yolo}.
 
@@
 A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector.
-Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{howard2017mobilenets}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}).
+Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}).
 A combination of the knob values is a video analytics \emph{configuration}.
@@
 Apparently, choosing different configurations will affect resource consumption and accuracy.
-For example, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources.
-However, choosing a simple model with low resolution can significantly reduce resource consumption, although it reduces the accuracy to some extent.
+When at a fixed frame rate, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources.
+Similarly, when using the same model with the same resolution, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy.
 Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy.
@@
 
-The \emph{best} configuration for a video analytics pipeline also varies over time, often at a timescale of minutes or even seconds \cite{jiang2018chameleon}.
+\begin{figure*}[!t]
+	\centerline{\includegraphics[width=0.9\linewidth]{figures/framework.pdf}}
+	%	\vspace{0.2cm}
+	\caption{Framework of AutoConfigure architecture}
+	\label{fig: framework}
+\end{figure*}
+
+%We use~\autoref{fig2} to support that, the data in this figure come from a real road.
+It can be found that with the decrease of frame rate, the resource consumption can be significantly reduced, but the decrease of accuracy is partly acceptable.
+
+%As shown in~\autoref{fig1}, at a fixed frame rate, using a complex model with high resolution (such as FasterRCNN+InceptionResnet 1024p) can obviously and accurately detect the target object, but it also requires more computing resources.
+However, when using the same model, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy.
+Another example is that choosing a simple model with low resolution (such as FasterRCNN+ResNet50 640p) can significantly reduce resource consumption, although it reduces the accuracy to some extent.
+
+%\begin{figure}[h]
+%\includegraphics[width=9cm,height=5cm]{figures/figure1.pdf}
+%\centering
+%\caption{The effect of different models and resolutions on accuracy and processing time at a fixed frame rate.}
+%\label{fig1}
+%\end{figure}
+%
+%\begin{figure}[h]
+%\includegraphics[width=9cm,height=5cm]{figures/figure2.pdf}
+%\centering
+%\caption{Under the best model, the accuracy and processing time vary with the different frame rate.}
+%\label{fig2}
+%\end{figure}
+
+The \emph{best} configuration for a video analytics services also varies over time, often at a timescale of minutes or even seconds \cite{jiang2018chameleon}.
 Hence, our goal is to find a range of ``most appropriate'' configurations that takes up the minimum amount of computing resources and is accurate to the desired threshold.
@@
 For a video analytics application, choosing the ``most appropriate'' configuration is a complicated decision-making problem, which is challenging to be solved by rules.
-An automatic approach is needed, one that is able to learn from video contents, to decide what is the best configuration for the current video content.
+An automatic approach is needed, one that is able to learn from video contexts, to decide what is the best configuration for the current video context.
 The reinforcement learning method is an excellent way to solve this unsupervised complex-environmental problem.
@@
 \begin{itemize}	
-\item \emph{The best configuration for a video analytics pipeline changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second.
-As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contents, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
+\item \emph{The best configuration for a video analytics services changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second.
+As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
 
@@
 \item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks.
-In practice, such a video analytics configuration is usually utilized in an online manner, and the solution has to learn from the video contents automatically.
+In practice, such a video analytics configuration is usually utilized in an online manner, and the solution has to learn from the video contexts automatically.
 \end{itemize}
 
-To address the above challenges, we present a content-driven automatic configuration framework based on reinforcement learning, called AutoConfigure, which can dynamically select the ``most appropriate'' configuration according to intrusive dynamics of video contents, thus solving this difficult optimal configuration decision problem in a very low-cost way.
-The main contributions of this paper are summarized as follows.
-\textcolor{note}{zhaoliang add more contributions}
+To address the above challenges, we present a context-driven automatic configuration framework based on reinforcement learning, called AutoConfigure, which can dynamically select the ``most appropriate'' configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a very low-cost way.
+A brief framework of AutoConfigure is shown in Figure~\ref{fig: framework}.
+\textcolor{note}{some description?} The main contributions of this paper are summarized as follows.
 
@@
 \item We design an interactive training environment that can be applied to different video analytics applications.
-We propose an asynchronous advantage actor-critic-based \cite{mnih2016asynchronous} agent to pick the best configuration for video analytics.
-Also, we define the elements of the RL-based approach, such as actions, states and rewards, to adapt the configuration to current video content.
+We propose an Deep Q-learning Network-based \cite{DQN} agent to pick the best configuration for video analytics.
+Also, we define the elements of the RL-based approach, such as actions, states and rewards, to adapt the configuration to current video context.
 
@@
 
-\item AutoConfigure can achieve xx-xx\% higher accuracy with the
+\item AutoConfigure can achieve 20-30\% higher accuracy with the
 same amount of resources, or achieve the same accuracy
-with only xx-xx\% of the resources. Furthermore, AutoConfigure proves to be more efficient than existing baselines by creating an overhead of less than xx\% to the overall video analytics pipeline.
+with only 50-70\% of the resources.
+Furthermore, AutoConfigure proves to be more efficient than existing baselines by creating an overhead of less than xx\%\textcolor{note}{(To be tested)} to the overall video analytics services.
 \end{itemize}

### 2020-11-26 paper/sections/relatedwork.tex
minor ab and intro
update 0908
ICME
design

@@
 
-\subsection{Configuration optimization} 
+%\subsection{Configuration optimization} 
 \subsection{Static configuration optimization}
-Several previous papers have considered optimizing video analytics pipelines by either adjusting the configuration knobs or training specialized NN models.
+Several previous papers have considered optimizing video analytics servicess by either adjusting the configuration knobs or training specialized NN models.
 VideoStorm \cite{zhang2017videostorm} profiles thousands of video analytics queries on live video streams over large clusters, achieving resource-quality tradeoff with multi-dimensional configurations.
@@
 These algorithms all profile and optimize video analytics only once at the beginning of the video.
-They do not handle changes in video stream content.
-But the optimal configurations do change over time because of the complex and changeable video stream contents.
+In their works, video is divided into pictures at a constant frame rate, and the work of video analyzing is regarded as a fixed task either.
+In other words, they do not handle changes in video stream context.
+But the optimal configurations do change over time because of the complex and changeable video stream contexts.
 
 \subsection{Dynamic configuration optimization}
-Some papers study how to dynamically optimize the configuration for video analytics when the video stream content changes.
+Some papers study how to dynamically optimize the configuration for video analytics when the video stream context changes.
 \cite{shen2017retrain_model} adaptively retrains the NN model to detect the set of popular objects as it changes over time in the video classification task.
@@
 enable a Big Data Cyber Security Analytics (BDCA) system to quickly adapt to the changes in security events data.
-JCAB \cite{wang2020jcab} jointly optimizes configuration adaption and bandwidth allocation to address several critical challenges in edge-based video analytics systems, including edge capacity limitation, unknown network variation, intrusive dynamics of video contents.
+JCAB \cite{wang2020jcab} jointly optimizes configuration adaption and bandwidth allocation to address several critical challenges in edge-based video analytics systems, including edge capacity limitation, unknown network variation, intrusive dynamics of video contexts.
 The online algorithm effectively balances analytics accuracy and energy consumption while keeping low system latency.
 \cite{argerich2019orchestration} leverages tabular Q-learning to adapt configuration, but their agent's states only consider last latency.
-Our framework pays attention to the complex and changeable video stream contents, and picks the best configuration according to current video content.
+Our framework pays attention to the complex and changeable video stream contexts, and picks the best configuration according to current video context.
 
-The closest work to ours is Chameleon \cite{jiang2018chameleon}, which dynamically picks the best configurations for video analytics pipelines, reducing resource consumption with little degradation in accuracy.
+The closest work to ours is Chameleon \cite{jiang2018chameleon}, which dynamically picks the best configurations for video analytics servicess, reducing resource consumption with little degradation in accuracy.
 They leverage temporal and spatial correlation to amortizes the cost of profiling over time and across multiple cameras, and exploit the knob independence to reduce the search space from exponential to linear.\cite{jiang2018chameleon} Notice that Chameleon still has non-trivial room for improvement compared to the optimal (idealized) performance, i.e.,

### 2020-11-27 paper/sections/introduction.tex
update introduction and using a new figure2

@@
 
-For the collected video, the classical computer vision and deep neural network technology are generally used for video analytics.
+%For the collected video, the classical computer vision and deep neural network technology are generally used for video analytics.
+
 A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector.
@@
 Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}.
+Different configurations directly affect accuracy and resource consumption.
+Using a fixed static high configuration can be very precise, but it can also be a huge drain on resource consumption.
+Similarly, specifying a low configuration will result in a significant reduction in accuracy.
 
-Apparently, choosing different configurations will affect resource consumption and accuracy.
+%Apparently, choosing different configurations will affect resource consumption and accuracy.
 When at a fixed frame rate, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources.

### 2020-11-28 paper/sections/design.tex
update introduction and using a new figure2
minor figure 2

@@
 \begin{figure*}[!t]
-	\centerline{\includegraphics[width=0.9\linewidth]{figures/DQN.jpg}}
+	\centerline{\includegraphics[width=0.9\linewidth]{figures/framework2.pdf}}
 	%	\vspace{0.2cm}
-	\caption{Applying reinforcement learning to automatic configuration.\textcolor{note}{redo}}
+	\caption{Applying reinforcement learning to automatic configuration}
 	\label{fig: DQN}
@@
 
-Figure~\ref{fig: DQN} summarizes how RL can be applied to automatic configuration.
-Briefly, it is a reinforcement learning-based system to train an agent to choose a proper configuration $ c $ for one video chunk to be inferenced.
+Figure~\ref{fig: DQN} summarizes how RL can be applied to the automatic configuration.
+Briefly, it is a reinforcement learning-based system to train an agent to choose a proper configuration $ c $ for one video chunk to inference.
 We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback in the following subsections.
@@
 
-For the cost of the object detection service, we use average GPU processing time per frame as the metric of resource consumption, because GPU is the dominant resource for the majority of video processing workloads.
+For the cost of the object detection service, we use average GPU processing time per frame as the metric of resource consumption because GPU is the dominant resource for the majority of video processing workloads.
 We also denote the metric of resource consumption as $ \hat{s}_{ic} $ that for an input video chunk $ x_i $ and a given configuration $ c $.
@@
 Therefore we can use the Deep Q-learning Network \cite{DQN} as the RL agent.
-But the naive Deep Q-learning Network can not work well in this task, because the state space of reinforcement learning is too large if we directly treat video chunk as the input.
+But the naive Deep Q-learning Network can not work well in this task because the state space of reinforcement learning is too large if we directly treat video chunk as the input.
 To preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge.

### 2020-12-02 paper/sections/design.tex
first draft

@@
 
+To automaticly choose different configuration for video stream, we divides the video into T-second intervals as video chunks, and profiles configurations for each video chunk.
 Without loss of generality, we denote the object detection service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input video chunk $ x_i $.
@@
 
-In our system, we define 48 discrete actions to indicate 48 configuration, and the specific configurations are provided in Section~\ref{Section: experiment}.
+In our system, we define 48 discrete actions to indicate 48 configuration, and the specific configurations are provided in Section~\ref{subsec: configuration}.
 We denote the \emph{action-value function} as $ Q(s, c; \theta) $ and the optimal compression quality level at time $ t $ as $  c_t = {\rm argmax}_cQ(s, c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
@@
 Therefore the overall reward $ r $ should be positively correlated with the accuracy $ \mathcal{A} $ while negatively with the resource consumption ratio $ \Delta s $.
-We introduce a linear factor $ \beta $ to form a linear combination $ r = \beta \mathcal{A} - (1-\beta) \Delta s  $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $.
+We introduce a balance factor $ \beta $ to form a linear combination $ r = \beta \mathcal{A} - (1-\beta) \Delta s  $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $.
 %% \\

### 2020-12-02 paper/sections/experiment.tex
first draft

--- 2020-11-14 paper/sections/experiment.tex
@@
-\section{Experiment}
+\section{Evaluation}
 \label{Section: experiment}
 
-\subsection{Experiment Setup}
-\textbf{Datasets:} Due to most of public sources datasets cannot fully satisfy all configuration choices, for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution, while others can guarantee resolution but cannot provide sufficient frame rate, but in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to use Youtube video as fellows.
-First, in order to eliminate the bias caused by Cookies and personal preferences, we use private browsing mode to search keywords (e.g., "drivecam highway hd").
+\subsection{Dataset and Metric}
+\label{subsec: datasets}
+
+Most public sources datasets cannot fully satisfy all configuration choices, for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution.
+In contrast, others can ensure resolution but cannot provide a sufficient frame rate.
+Still, in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to use Youtube video as fellows.
+We selected three datasets: M6, Duke, and Multi-Camera Dataset.
+M6 was taken from a traffic camera on the longest motorway in Britain.
+Duke is a video from a fixed camera placed at an intersection, and  the traffic flow in the video increases or decreases periodically as the traffic light change.
+Since the first two datasets were sourced from a fixed camera, to ensure that AutoConfigure still performs better when road conditions change dramatically, we used three videos collected from the dashcam.
+We combined them into one video, Multi-Camera Dataset.
+
+For metric, we use the F1 score as the accuracy and average GPU processing time per frame as the resource consumption, detail described in Section \ref{subsec: formulation}.
+%First, in order to eliminate the bias caused by Cookies and personal preferences, we use private browsing mode to search keywords (e.g., "drivecam highway hd").
 Second, manually delete irrelevant videos (e.g., ads for some driving recorders) and download videos that are longer than ten minutes.
@@
 Becaues of none of these videos contained ground truth, we used the data of the original video output from DNN as the tags to calculate the accuracy.
-For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 50$\%$ confidence score \textcolor{note}{this may need to be modified, chen tang}.
+For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 50$\%$ confidence score.Based on the above filtering strategy, we finally selected three datasets:
 
-Based on the above filtering strategy, we finally selected three datasets:
-
-M6: The M6 is the longest motorway in Britain and the most important road from the Midlands to the West Coast.
+%we selected three datasets:
+%M6: The M6 is the longest motorway in Britain and the most important road from the Midlands to the West Coast.
 Thousands of cars travel on it every day.
 This video was taken from a traffic camera, and its natural dynamics allows us to experiment with this video.
+%
+%Duke: Duke is a video from a fixed camera placed at an intersection.
+Because it is fixed in the middle of the intersection, the traffic flow in the video increases or decreases periodically as the traffic light change.
+%
+%Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.
 
-Duke: Duke is a video from a fixed camera placed at an intersection.
-Because it is fixed in the middle of the intersection, the traffic flow in the video increases or decreases periodically as the traffic light change.
+\begin{figure*}[!t]
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/m6.pdf}}
+		\centerline{(a) M6}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/duke.pdf}}
+		\centerline{(b) Duke}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
+		\centerline{(c) Multi-Camera Dataset}
+	\end{minipage}		
+	\caption{AutoConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different datasets. Each dot represents the results of running each solution.}
+	\label{fig: results}
+\end{figure*}
 
-Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.
-\subsection{Some results}
+\subsection{Configuration Selection}
+\label{subsec: configuration}
+We simulate the environment \cite{trade-offs} with three pretrained object detection models in Tensorflow, which are SSD+ResNet152V1, FasterRCNN+ResNet50V1, FasterRCNN+InceptionResNetV2.
+For each model, two kinds of image resolution, which is $1024\times1024$ and $640\times640$, can be picked up.
+In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}.
+We FFmpeg \cite{ffmpeg} to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model.
+The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.
+
+\subsection{Experiment Parameters}
+We apply a deep Q-learning network policy to train the agent.
+In the training procedure, we build up to eight independently identical environments for each data set to speed up the training and decrease the data's dependency.
+The leaning rate is set to 0.001.
+For each dataset, we train the agent 10 epochs and 1000 steps per epoch.
+Some important hyperparameters in our experiments are given in Table ~\ref{tab: parameters}.
+
+\begin{table}[!t]
+	\centering
+	\label{tab: parameters}
+	%     \begin{tabular}{llllll}
+	\resizebox{0.4\textwidth}{!}{
+		\begin{tabular}{cccccc}
+			\toprule
+			Notation          & Value & & & Notation     & Value  \\ \midrule
+			$\epsilon$    & 0.8    & & & $k_1$      & 3   \\
+			$\gamma$      & 0.9  & & & $k_2$    & 3    \\
+			$ \beta $ & 0.2,0.3,...,0.9 & & & $ T (train) $ & 1  \\
+			$ t(inference)  $  &  1   & & &   $ T (inference)  $  &  4      \\ 
+	\end{tabular}}
+	\caption{Experiment parameter}
+	\label{tab: parameters}
+	%	\vspace{-0.5cm}
+\end{table}
+
+\subsection{Experiment Results}
+We evaluate AutoConfigure on M6, Duke, and Multi-Camera Dataset video streams.
+Figure \ref{fig: results} shows that AutoConfigure consistently outperforms the baseline of static configuration (profiling configurations once at the beginning of a video stream) along with resource consumption and several accuracy metrics on different datasets.
+Each magenta dot represents one static configuration solution.
+These static configuration solutions including some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\}, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\}, \{SSD+ResNet152V1, 640p, 2fps\}, \{SSD+ResNet152V1, 640p, 5fps\}.
+Each blue dot represents one AutoConfigure configuration solution, which is dependent on the balance factor $\beta$ in reward function, presented in Section \ref{subsec: reward}.
+The detailed discussion about differents AutoConfigure solutions is in Section .
+As shown in Figure \ref{fig: results}(a)(b), AutoConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 50-80\% of the resources on a single-camera dataset.
+As shown in Figure \ref{fig: results}(c), the gap between AutoConfigure and static configuration is larger than Figure \ref{fig: results}(a)(b), indicating that AutoConfigure has a better improvement on the multi-camera situation.
+AutoConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 75-85\% of the resources on Multi-Camera Dataset.
+In a word, AutoConfigure can improve 10-35\% higher accuracy or save 50-85\% resource consumption.
+
+\subsubsection{Different AutoConfigure Solutions}
+\label{subsec: different sulutions}
+In the training phase, when using different balance factors $\beta$ in the reward function, we would obtain different agents (different automatic configuration strategies).
+In general, the $\beta$ is bigger, indicating the accuracy is more important relatively, and the agent would choose a more expensive configuration.
+In our experiment, we set $\beta$ is 0.2,0.3,...,0.9, and the results of different AutoConfigure solutions on Multi-Camera Dataset are listed in Table \ref{tab: different sulutions}.
+
+\begin{table}[!t]
+	\centering
+	%     \begin{tabular}{lll}
+	\resizebox{0.4\textwidth}{!}{
+		\begin{tabular}{ccc}
+			\toprule
+			balance factor $\beta$ & Avg GPU time per frame (second) & Avg F1 score  \\ \midrule
+			0.2          & 0.01384  &  0.64307            \\
+			0.3          & 0.03314  &  0.72008            \\
+			0.4          & 0.04921  &  0.78920            \\
+			0.5          & 0.05203  &  0.79096            \\
+			0.6          & 0.08479  &  0.80056            \\
+			0.7          & 0.17570  &  0.87731            \\
+			0.8          & 0.26511  &  0.93262            \\
+			0.9          & 0.30937  &  0.96537           \\
+			\bottomrule
+	\end{tabular}}
+	\caption{Resource consumption and F1 accuracy for different AutoConfigure solutions}
+	\label{tab: different sulutions}
+	% \vspace{-0.5cm}
+\end{table}
+
+Table \ref{tab: different sulutions} shows that when the $\beta$ increases, the resource consumption and the accuracy of the corresponding solution both would increase, indicating the AutoConfigure solutions of big $\beta$ would choose the more expensive configuration to inference.
+We can leverage this to train proper configuration strategy for different service demands, for example, using big $\beta$ for high-accuracy demand services and using small $\beta$ for low-accuracy demand services.
+
+\subsubsection{Profile Cost}
+\label{subsec: profile cost}
+Comparing to the static solution that profiles configurations once, in our solution, the video
+chunk is passed to the AutoConfigure firstly to estimate the configuration.
+Running this RL agent brings profile cost (extra resource consumption) to the whole system.
+In this section, we evaluate this profile cost.
+In the inference phase, we divide the video into $T$-second intervals as video chunks and use AutoConfigure to choose the proper configuration for the first t seconds of the video chunk.
+It then sticks with the chosen configuration for the rest of the video chunk, i.e., for $T-t$ seconds.
+We use T = 4 and t = 1 for our experiments.
+The profile cost, including the resource of extract $k_1$ embeddings and the cost of agent choosing actions.
+In our test, the average time of extract one embedding is 0.02s, and the average time of agent choosing action is 0.0006s, which can be ignored.
+We compute the ratio by dividing profile time into total inference time, which is equals the frame number multiply the average time per frame.
+The profile time is about 0.1-1\% of the overall video analytics resource consumption.
+The concrete ratio depends on the concrete AutoConfigure configuration solutions, such as the solutions listed in Table \ref{tab: different sulutions}.
 

### 2020-12-02 paper/sections/introduction.tex
first draft

@@
 \section{Introduction}
-\textcolor{note}{this section is too long}
 
@@
 Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}).
-A combination of the knob values is a video analytics \emph{configuration}.
-The configuration space grows \emph{exponentially} with the number of knobs and their values \cite{jiang2018chameleon}.
-Since video analytics applications demand intensive computation resources and high accuracy, we pay much attention to the consumption of resources in the calculation process and the accuracy of inference.
+A combination of the knob values is video analytics \emph{configuration}.
+The configuration space grows \emph{exponentially} with the number of knobs, and their values \cite{jiang2018chameleon}.
+Since video analytics applications demand intensive computation resources and high accuracy, we pay much attention to the consumption of resources in the calculation process and the inference accuracy.
 Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}.
@@
 Similarly, when using the same model with the same resolution, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy.
-Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy.
-And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout whole video.
-This can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.
+When the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a considerable reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve satisfactory accuracy.
+And in the case of highway video analytics, the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout the whole video.
+This can significantly reduce resource consumption but does not affect the accuracy of video analytics.
+
+%\begin{figure*}[!t]
+%	\centerline{\includegraphics[width=0.9\linewidth]{figures/framework.pdf}}
+%	%	\vspace{0.2cm}
+%	\caption{Framework of AutoConfigure architecture}
+%	\label{fig: framework}
+%\end{figure*}
 
 \begin{figure*}[!t]
-	\centerline{\includegraphics[width=0.9\linewidth]{figures/framework.pdf}}
-	%	\vspace{0.2cm}
-	\caption{Framework of AutoConfigure architecture}
+	%\begin{tabular}{cc}
+	\begin{minipage}{\linewidth}
+		\centerline{\includegraphics[width=0.8\linewidth]{figures/static_framework.pdf}}
+		\begin{center}
+			{(a) Static configuration solution: fixed configuration for video analytics services}
+		\end{center}
+		%        \vspace{0.3cm}
+	\end{minipage}
+	\vfill
+	\vspace{0.4cm}
+	\begin{minipage}{\linewidth}
+		\centerline{\includegraphics[width=0.8\linewidth]{figures/auto_framework.pdf}}
+		\vspace{0.2cm}
+		\begin{center}
+			{(b) AutoConfigure solution: context-driven automatic configuration framework}
+		\end{center}
+	\end{minipage}
+	%\end{tabular}
+	%\vspace{0.1cm}
+	\caption{Comparing to the static solution, our solution can update the configuration strategy based on the object detection model feedback}
 	\label{fig: framework}
@@
 %We use~\autoref{fig2} to support that, the data in this figure come from a real road.
-It can be found that with the decrease of frame rate, the resource consumption can be significantly reduced, but the decrease of accuracy is partly acceptable.
+It can be found that with the decrease of frame rate, the resource consumption can be significantly reduced, but the reduction of accuracy is partly acceptable.
 
@@
 Hence, our goal is to find a range of ``most appropriate'' configurations that takes up the minimum amount of computing resources and is accurate to the desired threshold.
-On the one hand, if one only profiles the processing pipeline to choose the best configuration \emph{once}, the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by picking a cheap configuration).
+On the one hand, like figure~\ref{fig: framework}(a), if one uses a static configuration solution (i.e.only profiles the processing pipeline to choose the best configuration \emph{once}), the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by selecting a cheap configuration).
 On the other hand, if one periodically profiles the processing pipeline to find an optimal resource-accuracy \emph{tradeoff} by exhaustive all configurations, it would be prohibitively expensive since the configuration space is extremely large, and thousands of configurations can be combined with just a few knobs.
+To tackle these challenges, we propose an automatic configuration approach, AutoConfigure, and the brief framework is shown in Figure~\ref{fig: framework}(b).
 
-%The most intuitive way to solve this problem is to find the best solution by exhaustive all configurations, but the number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs, so exhaustive configuration is a highly unrealistic approach.
+%The most intuitive way to solve this problem is to find the best solution by exhaustive all configurations.
+Still, the number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs, so exhaustive configuration is a highly unrealistic approach.
 
-For a video analytics application, choosing the ``most appropriate'' configuration is a complicated decision-making problem, which is challenging to be solved by rules.
-An automatic approach is needed, one that is able to learn from video contexts, to decide what is the best configuration for the current video context.
+For a video analytics application, choosing the ``most appropriate'' configuration is a complicated decision-making problem that is challenging to solve by rules.
+An automatic approach is needed to learn from video contexts to decide the best configuration for the current video context.
 The reinforcement learning method is an excellent way to solve this unsupervised complex-environmental problem.
@@
 
-%Also, one is not provided the well-labeled data on which configuration should be used in which time of the video, meaning this is an unsupervised learning task.
+%Also, one is not provided the well-labeled data on which configuration should be used at which time of the video, meaning this is an unsupervised learning task.
 
 \begin{itemize}	
-\item \emph{The best configuration for a video analytics services changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second.
+	\item \emph{The best configuration for video analytics services changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly require a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second.
 As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
@@
 	\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks.
-In practice, such a video analytics configuration is usually utilized in an online manner, and the solution has to learn from the video contexts automatically.
+In practice, such a video analytics configuration is usually utilized online, and the solution has to automatically learn from the video contexts.
 \end{itemize}
@@
 To address the above challenges, we present a context-driven automatic configuration framework based on reinforcement learning, called AutoConfigure, which can dynamically select the ``most appropriate'' configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a very low-cost way.
-A brief framework of AutoConfigure is shown in Figure~\ref{fig: framework}.
-\textcolor{note}{some description?} The main contributions of this paper are summarized as follows.
+The main contributions of this paper are summarized as follows.
 
@@
 	\item We design an interactive training environment that can be applied to different video analytics applications.
-We propose an Deep Q-learning Network-based \cite{DQN} agent to pick the best configuration for video analytics.
-Also, we define the elements of the RL-based approach, such as actions, states and rewards, to adapt the configuration to current video context.
+We propose a Deep Q-learning Network-based \cite{DQN} agent to pick the best video analytics configuration.
+Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to adapt the configuration to the current video context.
 
@@
 
-\item AutoConfigure can achieve 20-30\% higher accuracy with the
-same amount of resources, or achieve the same accuracy
-with only 50-70\% of the resources.
-Furthermore, AutoConfigure proves to be more efficient than existing baselines by creating an overhead of less than xx\%\textcolor{note}{(To be tested)} to the overall video analytics services.
+	\item AutoConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 50-85\% of the resources.
+AutoConfigure proves to be more efficient than static solutions and only creates an overhead of 0.1-1\% to the overall video analytics services.
 \end{itemize}

### 2020-12-02 paper/sections/relatedwork.tex
first draft

--- 2020-08-21 paper/sections/relatedwork.tex
@@
 
+%\subsection{Configuration optimization} 
 \subsection{Static configuration optimization}
-Several previous papers have considered optimizing video processing pipelines by either adjusting the configuration knobs or training specialized NN models.
+Several previous papers have considered optimizing video analytics services by either adjusting the configuration knobs or training specialized NN models.
 VideoStorm \cite{zhang2017videostorm} profiles thousands of video analytics queries on live video streams over large clusters, achieving resource-quality tradeoff with multi-dimensional configurations.
 VideoEdge \cite{hung2018videoedge} introduces \emph{dominant demand} to identify the best tradeoff between multiple resources and accuracy, and narrows the search space by identifying a ``Pareto ban'' of promising configurations.
-MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for
-deep stream processing under resource constraints.
-Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingest and video query.
-By tuning the share of computing resources of both phases, Focus achieves effective and flexible tradeoff of latency and accuracy of video analytics.
+MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints.
+Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingests and video query.
+By tuning the share of computing resources of both phases, Focus achieves an effective and flexible tradeoff of video analytics's latency and accuracy.
 These algorithms all profile and optimize video analytics only once at the beginning of the video.
-They do not handle changes in video stream content.
-But the optimal configurations do change over time because of the complex and changeable environment.
+In their works, video is divided into pictures at a constant frame rate, and the work of video analysis is regarded as a fixed task either.
+In other words, they do not handle changes in video stream context.
+But the optimal configurations do change over time because of the complex and changeable video stream contexts.
 
 \subsection{Dynamic configuration optimization}
-Some papers study how to dynamically optimize the configuration for video analytics when the video stream content changes.
-\cite{shen2017retrain_model} adaptively retrains the NN model to detect the set of popular objects as it changes over time in the video classification task.
+Some classic works study dynamic optimization problems.
+INFaaS \cite{romero2019infaas} automatically selects a model, hardware architecture, and any compiler optimizations and makes scaling and resource allocation decisions when application load varies and the available resources vary over time.
+QuickAdapt \cite{ullah2019quickadapt} uses descriptive statistics of security events data and fuzzy rules to enable a Big Data Cyber Security Analytics (BDCA) system to adapt to the changes in security events data quickly.
+Some papers study how to dynamically optimize the configuration for video analytics when the video stream context changes.
+JCAB \cite{wang2020jcab} jointly optimizes configuration adaption, and bandwidth allocation to address several critical challenges in edge-based video analytics systems, including edge capacity limitation, unknown network variation, intrusive dynamics of video contexts.
+Chameleon \cite{jiang2018chameleon} leverages temporal and spatial correlation to amortizes the cost of profiling over time and across multiple cameras and exploit the knob independence to reduce the search space from exponential to linear.
+Notice these reduce search space algorithm still try using various configurations to find the best configuration.
+Using different configuration would lead to extra expensive profiling costs.
+To significantly reduce the cost of profiling, we propose an automatic configuration algorithm.
+\cite{argerich2019orchestration} leverages tabular Q-learning to adapt configuration, but their agent's states only consider last latency.
+Our framework pays attention to the complex and changeable video stream contexts and picks the best configuration according to the current video context.
+
+Our solution, called AutoConfigure, leverages a reinforcement learning-agent to automatically choose the best configuration periodically, effectively improving the analytic accuracy while providing low-resource consumption.
+Furthermore, the extra cost of profiling is low since the agent's choosing time is hugely lower.
+
+%\cite{shen2017retrain_model} adaptively retrains the NN model to detect the set of popular objects as it changes over time in the video classification task.
 \cite{yang2019edge_coordinated} proposes an online video quality and computing resource configuration algorithm to gradually learn the optimal configuration strategy, effectively improving the analytic accuracy while providing the low-latency response.
-INFaaS \cite{romero2019infaas} automatically selects a model, hardware architecture, and any compiler optimizations, and makes scaling and resource allocation decisions when application load varies and the available resources vary over time.
-JCAB \cite{wang2020jcab} jointly optimizes
-configuration adaption and bandwidth allocation to address several critical challenges in edge-based video analytics systems,
-including edge capacity limitation, unknown network variation,
-intrusive dynamics of video contents. The online algorithm effectively balances analytics accuracy and energy
-consumption while keeping low system latency.
 
-The closest work to ours is Chameleon \cite{jiang2018chameleon}, which dynamically picks the best configurations for video analytics pipelines, reducing resource consumption
-with little degradation in accuracy.
-They leverage temporal and spatial correlation to amortizes the cost of profiling over time and across multiple cameras, and exploit the knob independence to reduce the search space from exponential to linear.
+%The online algorithm effectively balances analytics accuracy and energy consumption while keeping low system latency.
+
+%The closest work to ours is Chameleon \cite{jiang2018chameleon}, which dynamically picks the best configurations for video analytics services, reducing resource consumption with little degradation in accuracy.
+
+%\cite{jiang2018chameleon} Notice that Chameleon still has non-trivial room for improvement compared to the optimal (idealized) performance, i.e., periodic updating with zero profiling cost.
 Even the search space is linear, and the profiling cost is still expensive.
@@
 One profiling cost grows linear in the number of configuration knobs and the number of values per knob.
-The total profiling cost which is equal to one profiling cost multiply the number of profiling (5400) is also significantly high.
-\textcolor{note}{a little strange, can tangchen help amend?} Our solution called PerConfigure leverages a reinforcement learning-agent to choose the best configuration periodically, significantly reducing the cost of profiling since the choosing time is extremely lower.
+The total profiling cost is also significantly high, which is equal to one profiling cost multiply the number of profiling (5400).

### 2020-12-08 paper/sections/introduction.tex
update

@@
 
-The \emph{best} configuration for a video analytics services also varies over time, often at a timescale of minutes or even seconds \cite{jiang2018chameleon}.
-Hence, our goal is to find a range of ``most appropriate'' configurations that takes up the minimum amount of computing resources and is accurate to the desired threshold.
-On the one hand, like figure~\ref{fig: framework}(a), if one uses a static configuration solution (i.e.only profiles the processing pipeline to choose the best configuration \emph{once}), the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by selecting a cheap configuration).
+The \emph{best} configuration for video analysis services often varies in minutes or even seconds \cite{jiang2018chameleon}.
+%The \emph{best} configuration for a video analytics services also varies over time, often at a timescale of minutes or even seconds \cite{jiang2018chameleon}.
+Hence, we aim to find a range of ``most appropriate'' configurations that %takes up the
+minimize the consumption of computing resources and is accurate to the desired threshold.
+On the one hand, like figure~\ref{fig: framework}(a), if just use a unified static configuration solution (i.e.only profiles the processing pipeline to choose the best configuration \emph{once}), the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by selecting a cheap configuration).
 On the other hand, if one periodically profiles the processing pipeline to find an optimal resource-accuracy \emph{tradeoff} by exhaustive all configurations, it would be prohibitively expensive since the configuration space is extremely large, and thousands of configurations can be combined with just a few knobs.
@@
 \begin{itemize}	
-	\item \emph{The best configuration for video analytics services changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly require a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second.
-As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
+	\item \emph{The best configuration for video analytics services changes over time with the video content.} %environment.
+Video content varies with the real-world environment, so the best configuration is changing;
+%The real-world environment is non-stationary;
+ for instance, tracking vehicles when traffic moves quickly require a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, even second.
+As a dynamic video analytics configuration %solution
+application, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
 
-	\item \emph{How to significantly reduce the resource cost of periodic configuration profiling.} The cost of periodically profiling often exceeds any resource savings gained by adapting the best configurations we end up selecting.
+	\item \emph{How to significantly reduce the resource cost of periodic configuration profiling.} Because of the large configuration space, the cost of periodically profiling often exceeds any resource savings gained by adapting the best configurations we end up selecting.
 We leverage a Reinforcement Learning-based agent to automatically pick the best configuration periodically, dramatically reducing the profiling cost.
 
-	\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks.
+	\item \emph{Lack of well-labeled training data.} In our case, there was no well-marked data that indicated which configuration should be choosed at which time of the video, as is the case with traditional deep learning tasks.%In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks.
 In practice, such a video analytics configuration is usually utilized online, and the solution has to automatically learn from the video contexts. 

### 2020-12-09 paper/sections/design.tex
major experiment

@@
 
-To address this challenges, we extract the top $k_1$ representative images from each chunk as spatial correlations of video chunk.
+To address this challenges, we extract the top $k_1$ representative images from each chunk as spatial features of video chunk.
 We use a pre-trained small neural network to extract the structural information embeddings $ \{e_1,e_2,...,e_{k_1}\} $ of the images to reduce the input dimension and accelerate the training procedure.
@@
 In this work, we use the early convolution layers of MobileNetV2~\cite{MobileNetV2} as the image feature extractor $ \mathcal{E}(\cdot) $ for its efficiency in image classification.
-To extract the temporal correlations of video chunk, we obtain $ \{\hat{e}_1,\hat{e}_2,...,\hat{e}_{{k_1}-1}\} $ by each embedding subtracting previous embedding.
+To extract the temporal features of video chunk, we obtain $ \{\hat{e}_1,\hat{e}_2,...,\hat{e}_{{k_1}-1}\} $ by each embedding subtracting previous embedding.
 Besides, we record the last $k_2$ configurations $ \{c_1,c_2,...,c_{k_2}\} $.

### 2020-12-09 paper/sections/experiment.tex
major experiment

@@
 In contrast, others can ensure resolution but cannot provide a sufficient frame rate.
-Still, in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to use Youtube video as fellows.
+Still, in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to search keywords (e.g., "highway traffic") on Youtube and download videos that meet the resolution and frame rate requirements.
 We selected three datasets: M6, Duke, and Multi-Camera Dataset.
@@
 Duke is a video from a fixed camera placed at an intersection, and the traffic flow in the video increases or decreases periodically as the traffic light change.
-Since the first two datasets were sourced from a fixed camera, to ensure that AutoConfigure still performs better when road conditions change dramatically, we used three videos collected from the dashcam.
-We combined them into one video, Multi-Camera Dataset.
+Since the first two datasets were sourced from a fixed camera, to ensure that AutoConfigure performs better in multi-camera inference, we combine three videos collected from different locations into one video dataset, Multi-Camera Dataset.
+The exact content of this dataset varies significantly over time and across space.
 
-For metric, we use the F1 score as the accuracy and average GPU processing time per frame as the resource consumption, detail described in Section \ref{subsec: formulation}.
-%First, in order to eliminate the bias caused by Cookies and personal preferences, we use private browsing mode to search keywords (e.g., "drivecam highway hd").
+For metric, we use the F1 score as the accuracy and average GPU processing time per frame as the resource consumption, detail described in Section \ref{subsec: formulation}. F1 score
+is the harmonic mean of precision and recall, where the precision is true positives divided by the detected objects, and the recall is true positives divided by the ground truth objects.
+We identify true positives using two conditions, an abounding box-based condition (only check the classified label) and a label-based condition (check the classified label and spatial overlap \cite{overlap}), consistent with prior work \cite{jiang2018chameleon,noscope}.
+Both metrics are useful in real video analytics services and used in our experiments.
+%, consistent with prior work [24, 32].
+%First, to eliminate the bias caused by Cookies and personal preferences, we use private browsing mode to search keywords (e.g., "drivecam highway hd").
 Second, manually delete irrelevant videos (e.g., ads for some driving recorders) and download videos that are longer than ten minutes.
-In addition, these videos need to be as dynamic as the real world, such as not standing still for too long.
-Becaues of none of these videos contained ground truth, we used the data of the original video output from DNN as the tags to calculate the accuracy.
+These videos need to be as dynamic as the real world, such as not standing still for too long.
+Because none of these videos contained ground truth, we used the original video output data from DNN as the tags to calculate the accuracy.
 For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 50$\%$ confidence score.Based on the above filtering strategy, we finally selected three datasets:
@@
 		\centerline{\includegraphics[width=6.5cm]{figures/m6.pdf}}
-		\centerline{(a) M6}
+		\centerline{(a) M6 (Bounding box-based)}
 	\end{minipage}
@@
 		\centerline{\includegraphics[width=6.5cm]{figures/duke.pdf}}
-		\centerline{(b) Duke}
+		\centerline{(b) Duke (Bounding box-based)}
 	\end{minipage}
@@
 		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
-		\centerline{(c) Multi-Camera Dataset}
+		\centerline{(c) Multi-Camera Dataset (Bounding box-based)}
 	\end{minipage}
-	\caption{AutoConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different datasets. Each dot represents the results of running each solution.}
+	\vfill
+	\vspace{0.4cm}
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/m6_label.pdf}}
+		\centerline{(d) M6 (label-based)}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/duke_label.pdf}}
+		\centerline{(e) Duke (label-based)}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
+		\centerline{(f) Multi-Camera Dataset (label-based) \textcolor{note}{running}}
+	\end{minipage}		
+	\caption{AutoConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different metrics on different datasets.
+Each dot represents the results of running each solution.}
 	\label{fig: results}
@@
 			$\gamma$      & 0.9  & & & $k_2$    & 3    \\
-			$ \beta $ & 0.2,0.3,...,0.9 & & & $ T (train) $ & 1  \\
+			$ \beta $ & 0.2,0.3,...,0.7 & & & $ T (train) $ & 1  \\
 			$ t(inference)  $  &  1   & & &   $ T (inference)  $  &  4      \\ 
@@
 \subsection{Experiment Results}
-We evaluate AutoConfigure on M6, Duke, and Multi-Camera Dataset video streams.
-Figure \ref{fig: results} shows that AutoConfigure consistently outperforms the baseline of static configuration (profiling configurations once at the beginning of a video stream) along with resource consumption and several accuracy metrics on different datasets.
+\begin{figure*}[!t]
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/Westbound.pdf}}
+		\centerline{(a) Camera 1 (Bounding box-based)}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/Eastbound.pdf}}
+		\centerline{(b) Camera 2 (Bounding box-based)}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/Rear.pdf}}
+		\centerline{(c) Camera 3 (Bounding box-based)}
+	\end{minipage}		
+	\caption{AutoConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different cameras.}
+	\label{fig: 3dataset results}
+\end{figure*}
+
+We use bounding box-based and label-based metric to evaluate AutoConfigure on M6, Duke, and Multi-Camera Dataset video streams.
+Figure \ref{fig: results} shows that AutoConfigure consistently outperforms the baseline of static configuration (profiling configurations once at the beginning of a video stream) along with resource consumption and two accuracy metrics on different datasets.
 Each magenta dot represents one static configuration solution.
@@
 Each blue dot represents one AutoConfigure configuration solution, which is dependent on the balance factor $\beta$ in reward function, presented in Section \ref{subsec: reward}.
-The detailed discussion about differents AutoConfigure solutions is in Section .
-As shown in Figure \ref{fig: results}(a)(b), AutoConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 50-80\% of the resources on a single-camera dataset.
-As shown in Figure \ref{fig: results}(c), the gap between AutoConfigure and static configuration is larger than Figure \ref{fig: results}(a)(b), indicating that AutoConfigure has a better improvement on the multi-camera situation.
-AutoConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 75-85\% of the resources on Multi-Camera Dataset.
-In a word, AutoConfigure can improve 10-35\% higher accuracy or save 50-85\% resource consumption.
+The detailed discussion about differents AutoConfigure solutions is in Section \ref{subsec: different sulutions}.
+As shown in Figure \ref{fig: results}(a)(d), AutoConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 60-80\% of the resources on the M6 dataset.
+As shown in Figure \ref{fig: results}(b)(e), AutoConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 80-90\% of the resources on a Duke dataset.
+As shown in Figure \ref{fig: results}(c)(f), AutoConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 75-85\% of the resources on Multi-Camera Dataset.
+In a word, AutoConfigure can improve 10-35\% higher accuracy or save 60-90\% resource consumption.
 
@@
 In general, the $\beta$ is bigger, indicating the accuracy is more important relatively, and the agent would choose a more expensive configuration.
-In our experiment, we set $\beta$ is 0.2,0.3,...,0.9, and the results of different AutoConfigure solutions on Multi-Camera Dataset are listed in Table \ref{tab: different sulutions}.
+In our experiment, we set $\beta$ is 0.2,0.3,...,0.7, and the results of different AutoConfigure solutions on Multi-Camera Dataset are listed in Table \ref{tab: different sulutions}.
 
@@
 			0.3          & 0.03314  &  0.72008            \\
-			0.4          & 0.04921  &  0.78920            \\
-			0.5          & 0.05203  &  0.79096            \\
-			0.6          & 0.08479  &  0.80056            \\
-			0.7          & 0.17570  &  0.87731            \\
-			0.8          & 0.26511  &  0.93262            \\
-			0.9          & 0.30937  &  0.96537           \\
+			0.4          & 0.05203  &  0.79096            \\
+			0.5          & 0.08479  &  0.80056            \\
+			0.6          & 0.17570  &  0.87731            \\
+			0.7          & 0.26511  &  0.93262            \\
 			\bottomrule
@@
 
-Table \ref{tab: different sulutions} shows that when the $\beta$ increases, the resource consumption and the accuracy of the corresponding solution both would increase, indicating the AutoConfigure solutions of big $\beta$ would choose the more expensive configuration to inference.
+Table \ref{tab: different sulutions} shows that when the $\beta$ increases, the resource consumption and the accuracy of the corresponding solution would increase, indicating the AutoConfigure solutions of big $\beta$ would choose the more expensive configuration to inference.
 We can leverage this to train proper configuration strategy for different service demands, for example, using big $\beta$ for high-accuracy demand services and using small $\beta$ for low-accuracy demand services.
+
+\subsubsection{Superior Performance on Multi-camera Situation}
+\label{subsec: superior performance}
+
+To compare AutoConfigure's performance on single-camera inference and multi-camera inference, we respectively train and test the agent on each single-camera dataset of Multi-Camera Dataset.
+Figure \ref{fig: 3dataset results}(a)(b)(c) shows that AutoConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 50-60\% of the resources on a single-camera inference.
+As shown in Figure \ref{fig: results}(c), the gap between AutoConfigure and static configuration is larger than Figure \ref{fig: 3dataset results}(a)(b)(c), indicating that AutoConfigure has a better improvement on the multi-camera situation.
+AutoConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or reach higher accuracy with only 75-85\% of the resources on multi-camera inference.
+AutoConfigure achieves superior performance on multi-camera inference than single-camera inference.
+Instead of the static solution using fixed configuration on different situations, AutoConfigure can choose a proper configuration for different situations since the exact contents of the video are different in different locations.
+It proves that our solution can pick the proper configuration according to intrusive dynamics of video contexts, including spatial and temporal features.
 

### 2020-12-09 paper/sections/introduction.tex
major experiment

@@
 
-	\item AutoConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 50-85\% of the resources.
+	\item AutoConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 60-90\% of the resources.
 AutoConfigure proves to be more efficient than static solutions and only creates an overhead of 0.1-1\% to the overall video analytics services.

### 2020-12-09 paper/sections/experiment.tex
minor experiment

@@
 	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
-		\centerline{(f) Multi-Camera Dataset (label-based) \textcolor{note}{running}}
+		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear_label.pdf}}
+		\centerline{(f) Multi-Camera Dataset (label-based)}
 	\end{minipage}		
@@
 In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}.
-We FFmpeg \cite{ffmpeg} to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model.
+We use FFmpeg \cite{ffmpeg} to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model.
 The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.
@@
 Each magenta dot represents one static configuration solution.
-These static configuration solutions including some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\}, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\}, \{SSD+ResNet152V1, 640p, 2fps\}, \{SSD+ResNet152V1, 640p, 5fps\}.
+These static configuration solutions include some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\} and so on, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\}, \{SSD+ResNet152V1, 640p, 2fps\}, \{SSD+ResNet152V1, 640p, 5fps\} and so on.
 Each blue dot represents one AutoConfigure configuration solution, which is dependent on the balance factor $\beta$ in reward function, presented in Section \ref{subsec: reward}.

### 2020-12-10 paper/sections/introduction.tex
major abstract and intro

--- 2020-12-02 paper/sections/introduction.tex
@@
 Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}).
-A combination of the knob values is video analytics \emph{configuration}.
-The configuration space grows \emph{exponentially} with the number of knobs, and their values \cite{jiang2018chameleon}.
-Since video analytics applications demand intensive computation resources and high accuracy, we pay much attention to the consumption of resources in the calculation process and the inference accuracy.
-Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}.
+A combination of the knob values is video analytics \emph{configuration}, and the configuration space grows \emph{exponentially} with the number of knobs, and their values \cite{jiang2018chameleon}.
+
 Different configurations directly affect accuracy and resource consumption.
-Using a fixed static high configuration can be very precise, but it can also be a huge drain on resource consumption.
-Similarly, specifying a low configuration will result in a significant reduction in accuracy.
-
-%Apparently, choosing different configurations will affect resource consumption and accuracy.
-When at a fixed frame rate, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources.
-Similarly, when using the same model with the same resolution, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy.
-When the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a considerable reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve satisfactory accuracy.
-And in the case of highway video analytics, the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout the whole video.
-This can significantly reduce resource consumption but does not affect the accuracy of video analytics.
-
-%\begin{figure*}[!t]
-%	\centerline{\includegraphics[width=0.9\linewidth]{figures/framework.pdf}}
-%	%	\vspace{0.2cm}
-%	\caption{Framework of AutoConfigure architecture}
-%	\label{fig: framework}
-%\end{figure*}
+The best configuration is the one with the lowest resource demand whose accuracy is over the desired threshold, whcih can optimize the \emph{trade-off} between accuracy and energy consumption.
+The \emph{best} configuration for video analysis services often varies in minutes or even seconds \cite{jiang2018chameleon}.
+As shown in figure~\ref{fig: framework}(a), if one just uses a fixed static expensive configuration (e.g.
+only profiles the processing pipeline \emph{once} to choose high frame rate and resolution) can be very precise, but it can also be a huge drain on resource consumption.
+Similarly, specifying a fixed static cheap (e.g., low resolution and small model) configuration will significantly reduce accuracy.
+To tackle these challenges, we propose an adaptive configuration approach, AdaConfigure, and the brief framework is shown in Figure~\ref{fig: framework}(b).
+In our solution, we tackle the following design challenges.
 
@@
 		\begin{center}
-			{(b) AutoConfigure solution: context-driven automatic configuration framework}
+			{(b) AdaConfigure solution: reinforcement learning-based adaptive configuration framework}
 		\end{center}
@@
 	%\vspace{0.1cm}
-	\caption{Comparing to the static solution, our solution can update the configuration strategy based on the object detection model feedback}
+	\caption{Comparing to the static solution, our solution can adaptively update the configuration strategy based on the object detection model feedback}
+	%	\caption{Comparing to the static solution, our solution can update the configuration strategy based on the object detection model feedback}
 	\label{fig: framework}
 \end{figure*}
+
+\begin{itemize}	
+	\item \emph{Choosing the best configuration is a complicated decision-making problem that is challenging to solve by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space.
+For instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but each condition may vary by hour, minute, even second.
+Spatially, the characteristics of video content are different in different locations.
+For instance, cameras in downtown areas show more cars than the other cameras deployed in the suburbs.
+It is hard to make an exact rule to choose a configuration for the current context by profiling such complicated video's characteristics.
+	%As a dynamic video analytics configuration %solution
+	%application, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
+
+	\item \emph{Adaptive configuration would cause a huge extra overhead.} The number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs \cite{jiang2018chameleon}.
+So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations.
+To significantly reduce the resource cost for adaptive configuration profiling requires one solution that automaticly choose a configuration instead of manually trying using various configurations, which is challengling to previous studies including \cite{wang2020jcab,jiang2018chameleon}, since their approach pay attention to reduce search space algorithm and still try using various configurations to find the best configuration.
+
+	%We leverage a Reinforcement Learning-based agent to adaptively pick the best configuration periodically, dramatically reducing the profiling cost. 
+	%How to significantly reduce the resource cost of periodic configuration profiling.
+
+	%\item \emph{Lack of well-labeled training data.} In our case, there was no well-marked data that indicated which configuration should be choosed at which time of the video, as is the case with traditional deep learning tasks.%In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks.
+In practice, such a video analytics configuration is usually utilized online, and the solution has to adaptively learn from the video contexts.
+\end{itemize}
+
+To address the above complicated decision-making problem and reduce the huge extra overhead of manually trying using various configurations, we carefully design an adaptive configuration framework based on reinforcement learning, which is an excellent approach to solve this unsupervised complex-environmental problem.
+AutoConfigure can adaptively and automatically select the best configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a very low-cost way.
+To the best of our knowledge, we are the first to propose an adaptive video configuration solution that adaptively and automatically chooses a configuration according to the current video context.
+The main contributions of this paper are summarized as follows.
+
+\begin{itemize}	
+	\item We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to intrusive dynamics of video contexts.
+Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to adapt the configuration to the current video context.
+In the state design, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance on the multi-camera situation.
+In the reward desgin, we carefully consider both inference accuracy and computation resources to assess each configuration's impact.
+Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents.
+In our design, our solution can adaptively update configuration strategy over time, and it adaptive to different location-camera inferences and different accuracy-demand services.
+	%	 We design an interactive training environment that can be applied to different video analytics applications.
+	%	\item We build a reinforcement learning-based framework to train the agent in the above environment.
+The agent can learn to choose a ``most appropriate'' configuration for each timestamp of video analytics after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and resources.
+
+	\item We leverage dividing video strategy and the extremely short choosing action time of agent to reduce profiling cost.
+In the evaluation, AdaConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 60-90\% of the resources.
+Our solution proves to be more efficient than static solutions and only creates an overhead of 0.1-1\% to the overall video analytics services.
+\end{itemize}
+
+%The rest of this paper is organized as follows.
+We discuss related works in Section \ref{Section: related_works}.
+We present our framework and detailed design in Section \ref{Section: design}.
+We present our solution's performance in Section \ref{Section: evaluation} and conclude the paper in Section \ref{Section: conclusion}.
+
+%Since video analytics applications demand intensive computation resources and high accuracy, we pay much attention to the consumption of resources in the calculation process and the inference accuracy.
+Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}.
+
+%Apparently, choosing different configurations will affect resource consumption and accuracy.
+When at a fixed frame rate, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources.
+Similarly, when using the same model with the same resolution, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy.
+When the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a considerable reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve satisfactory accuracy.
+And in the case of highway video analytics, the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout the whole video.
+This can significantly reduce resource consumption but does not affect the accuracy of video analytics.
+
+%\begin{figure*}[!t]
+%	\centerline{\includegraphics[width=0.9\linewidth]{figures/framework.pdf}}
+%	%	\vspace{0.2cm}
+%	\caption{Framework of AutoConfigure architecture}
+%	\label{fig: framework}
+%\end{figure*}
 
@@
 
-The \emph{best} configuration for a video analytics services also varies over time, often at a timescale of minutes or even seconds \cite{jiang2018chameleon}.
-Hence, our goal is to find a range of ``most appropriate'' configurations that takes up the minimum amount of computing resources and is accurate to the desired threshold.
-On the one hand, like figure~\ref{fig: framework}(a), if one uses a static configuration solution (i.e.only profiles the processing pipeline to choose the best configuration \emph{once}), the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by selecting a cheap configuration).
+%Like figure~\ref{fig: framework}(a), if one just use a unified static configuration solution (i.e.only profiles the processing pipeline to choose the best configuration \emph{once}), the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by selecting a cheap configuration).
+
+%Hence, we aim to find a range of ``most appropriate'' configurations that %takes up the
+%minimize the consumption of computing resources and is accurate to the desired threshold.
+On the one hand, like figure~\ref{fig: framework}(a), if one just use a unified static configuration solution (i.e.only profiles the processing pipeline to choose the best configuration \emph{once}), the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by selecting a cheap configuration).
 On the other hand, if one periodically profiles the processing pipeline to find an optimal resource-accuracy \emph{tradeoff} by exhaustive all configurations, it would be prohibitively expensive since the configuration space is extremely large, and thousands of configurations can be combined with just a few knobs.
-To tackle these challenges, we propose an automatic configuration approach, AutoConfigure, and the brief framework is shown in Figure~\ref{fig: framework}(b).
+To tackle these challenges, we propose an adaptive configuration approach, AutoConfigure, and the brief framework is shown in Figure~\ref{fig: framework}(b).
 
@@
 
-For a video analytics application, choosing the ``most appropriate'' configuration is a complicated decision-making problem that is challenging to solve by rules.
-An automatic approach is needed to learn from video contexts to decide the best configuration for the current video context.
+%For a video analytics application, choosing the ``most appropriate'' configuration is a complicated decision-making problem that is challenging to solve by rules.
+An adaptive approach is needed to learn from video contexts to decide the best configuration for the current video context.
 The reinforcement learning method is an excellent way to solve this unsupervised complex-environmental problem.
@@
 %Also, one is not provided the well-labeled data on which configuration should be used at which time of the video, meaning this is an unsupervised learning task.
-
-\begin{itemize}	
-	\item \emph{The best configuration for video analytics services changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly require a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second.
-As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
-
-	\item \emph{How to significantly reduce the resource cost of periodic configuration profiling.} The cost of periodically profiling often exceeds any resource savings gained by adapting the best configurations we end up selecting.
-We leverage a Reinforcement Learning-based agent to automatically pick the best configuration periodically, dramatically reducing the profiling cost.
-
-	\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks.
-In practice, such a video analytics configuration is usually utilized online, and the solution has to automatically learn from the video contexts.
-\end{itemize}
-
-To address the above challenges, we present a context-driven automatic configuration framework based on reinforcement learning, called AutoConfigure, which can dynamically select the ``most appropriate'' configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a very low-cost way.
-The main contributions of this paper are summarized as follows.
-
-\begin{itemize}	
-	\item We design an interactive training environment that can be applied to different video analytics applications.
-We propose a Deep Q-learning Network-based \cite{DQN} agent to pick the best video analytics configuration.
-Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to adapt the configuration to the current video context.
-
-	\item We build a reinforcement learning-based framework to train the agent in the above environment.
-The agent can learn to choose a ``most appropriate'' configuration for each timestamp of video analytics after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and resources.
-
-	\item AutoConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 50-85\% of the resources.
-AutoConfigure proves to be more efficient than static solutions and only creates an overhead of 0.1-1\% to the overall video analytics services.
-\end{itemize}
-
-%The rest of this paper is organized as follows.
-We discuss related works in Section \ref{Section: related_works}.
-We present our framework and detailed design in Section \ref{Section: design}.
-We present our solution's performance in Section \ref{Section: evaluation} and conclude the paper in Section \ref{Section: conclusion}.

### 2020-12-10 paper/sections/experiment.tex
minor evaluation

@@
 Duke is a video from a fixed camera placed at an intersection, and the traffic flow in the video increases or decreases periodically as the traffic light change.
-Since the first two datasets were sourced from a fixed camera, to ensure that AutoConfigure performs better in multi-camera inference, we combine three videos collected from different locations into one video dataset, Multi-Camera Dataset.
+Since the first two datasets were sourced from a fixed camera, to ensure that AdaConfigure performs better in multi-camera inference, we combine three videos collected from different locations into one video dataset, Multi-Camera Dataset.
 The exact content of this dataset varies significantly over time and across space.
@@
 %
-%Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.
+%Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AdaConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.
 
@@
 	\end{minipage}		
-	\caption{AutoConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different metrics on different datasets.
+	\caption{AdaConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different metrics on different datasets.
 Each dot represents the results of running each solution.}
@@
 	\end{minipage}		
-	\caption{AutoConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different cameras.}
+	\caption{AdaConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different cameras.}
 	\label{fig: 3dataset results}
@@
 
-We use bounding box-based and label-based metric to evaluate AutoConfigure on M6, Duke, and Multi-Camera Dataset video streams.
-Figure \ref{fig: results} shows that AutoConfigure consistently outperforms the baseline of static configuration (profiling configurations once at the beginning of a video stream) along with resource consumption and two accuracy metrics on different datasets.
+We use bounding box-based and label-based metric to evaluate AdaConfigure on M6, Duke, and Multi-Camera Dataset video streams.
+Figure \ref{fig: results} shows that AdaConfigure consistently outperforms the baseline of static configuration (profiling configurations once at the beginning of a video stream) along with resource consumption and two accuracy metrics on different datasets.
 Each magenta dot represents one static configuration solution.
 These static configuration solutions include some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\} and so on, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\}, \{SSD+ResNet152V1, 640p, 2fps\}, \{SSD+ResNet152V1, 640p, 5fps\} and so on.
-Each blue dot represents one AutoConfigure configuration solution, which is dependent on the balance factor $\beta$ in reward function, presented in Section \ref{subsec: reward}.
-The detailed discussion about differents AutoConfigure solutions is in Section \ref{subsec: different sulutions}.
-As shown in Figure \ref{fig: results}(a)(d), AutoConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 60-80\% of the resources on the M6 dataset.
-As shown in Figure \ref{fig: results}(b)(e), AutoConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 80-90\% of the resources on a Duke dataset.
-As shown in Figure \ref{fig: results}(c)(f), AutoConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 75-85\% of the resources on Multi-Camera Dataset.
-In a word, AutoConfigure can improve 10-35\% higher accuracy or save 60-90\% resource consumption.
+Each blue dot represents one AdaConfigure configuration solution, which is dependent on the balance factor $\beta$ in reward function, presented in Section \ref{subsec: reward}.
+The detailed discussion about differents AdaConfigure solutions is in Section \ref{subsec: different sulutions}.
+As shown in Figure \ref{fig: results}(a)(d), AdaConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 60-80\% of the resources on the M6 dataset.
+As shown in Figure \ref{fig: results}(b)(e), AdaConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 80-90\% of the resources on a Duke dataset.
+As shown in Figure \ref{fig: results}(c)(f), AdaConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 75-85\% of the resources on Multi-Camera Dataset.
+In a word, AdaConfigure can improve 10-35\% higher accuracy or save 60-90\% resource consumption.
 
-\subsubsection{Different AutoConfigure Solutions}
+\subsubsection{Superior Performance on Multi-camera Situation}
+\label{subsec: superior performance}
+
+To compare AdaConfigure's performance on single-camera inference and multi-camera inference, we respectively train and test the agent on each single-camera dataset of Multi-Camera Dataset.
+Figure \ref{fig: 3dataset results}(a)(b)(c) shows that AdaConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 50-60\% of the resources on a single-camera inference.
+As shown in Figure \ref{fig: results}(c), the gap between AdaConfigure and static configuration is larger than Figure \ref{fig: 3dataset results}(a)(b)(c), indicating that AdaConfigure has a better improvement on the multi-camera situation.
+AdaConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or reach higher accuracy with only 75-85\% of the resources on multi-camera inference.
+AdaConfigure achieves superior performance on multi-camera inference than single-camera inference.
+Instead of the static solution using fixed configuration on different situations, AdaConfigure can choose a proper configuration for different situations since the exact spatial characteristics of the video contents are different in different locations.
+It proves that our solution can pick the proper configuration according to intrusive dynamics of video contexts, including spatial and temporal features.
+
+\subsubsection{Different AdaConfigure Solutions to Meet Different Services}
 \label{subsec: different sulutions}
@@
 In general, the $\beta$ is bigger, indicating the accuracy is more important relatively, and the agent would choose a more expensive configuration.
-In our experiment, we set $\beta$ is 0.2,0.3,...,0.7, and the results of different AutoConfigure solutions on Multi-Camera Dataset are listed in Table \ref{tab: different sulutions}.
+In our experiment, we set $\beta$ is 0.2,0.3,...,0.7, and the results of different AdaConfigure solutions on Multi-Camera Dataset are listed in Table \ref{tab: different sulutions}.
 
@@
 	\end{tabular}}
-	\caption{Resource consumption and F1 accuracy for different AutoConfigure solutions}
+	\caption{Resource consumption and F1 accuracy for different AdaConfigure solutions}
 	\label{tab: different sulutions}
@@
 
-Table \ref{tab: different sulutions} shows that when the $\beta$ increases, the resource consumption and the accuracy of the corresponding solution would increase, indicating the AutoConfigure solutions of big $\beta$ would choose the more expensive configuration to inference.
+Table \ref{tab: different sulutions} shows that when the $\beta$ increases, the resource consumption and the accuracy of the corresponding solution would increase, indicating the AdaConfigure solutions of big $\beta$ would choose the more expensive configuration to inference.
 We can leverage this to train proper configuration strategy for different service demands, for example, using big $\beta$ for high-accuracy demand services and using small $\beta$ for low-accuracy demand services.
 
-\subsubsection{Superior Performance on Multi-camera Situation}
-\label{subsec: superior performance}
-
-To compare AutoConfigure's performance on single-camera inference and multi-camera inference, we respectively train and test the agent on each single-camera dataset of Multi-Camera Dataset.
-Figure \ref{fig: 3dataset results}(a)(b)(c) shows that AutoConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 50-60\% of the resources on a single-camera inference.
-As shown in Figure \ref{fig: results}(c), the gap between AutoConfigure and static configuration is larger than Figure \ref{fig: 3dataset results}(a)(b)(c), indicating that AutoConfigure has a better improvement on the multi-camera situation.
-AutoConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or reach higher accuracy with only 75-85\% of the resources on multi-camera inference.
-AutoConfigure achieves superior performance on multi-camera inference than single-camera inference.
-Instead of the static solution using fixed configuration on different situations, AutoConfigure can choose a proper configuration for different situations since the exact contents of the video are different in different locations.
-It proves that our solution can pick the proper configuration according to intrusive dynamics of video contexts, including spatial and temporal features.
-
-\subsubsection{Profile Cost}
+\subsubsection{Low Profiling Cost of Adaptive Configuration}
 \label{subsec: profile cost}
 Comparing to the static solution that profiles configurations once, in our solution, the video
-chunk is passed to the AutoConfigure firstly to estimate the configuration.
+chunk is passed to the AdaConfigure firstly to estimate the configuration.
 Running this RL agent brings profile cost (extra resource consumption) to the whole system.
 In this section, we evaluate this profile cost.
-In the inference phase, we divide the video into $T$-second intervals as video chunks and use AutoConfigure to choose the proper configuration for the first t seconds of the video chunk.
+In the inference phase, we divide the video into $T$-second intervals as video chunks and use AdaConfigure to choose the proper configuration for the first t seconds of the video chunk.
 It then sticks with the chosen configuration for the rest of the video chunk, i.e., for $T-t$ seconds.
@@
 We compute the ratio by dividing profile time into total inference time, which is equals the frame number multiply the average time per frame.
-The profile time is about 0.1-1\% of the overall video analytics resource consumption.
-The concrete ratio depends on the concrete AutoConfigure configuration solutions, such as the solutions listed in Table \ref{tab: different sulutions}.
+The profile cost is about 0.2-2\% of the overall video analytics resource consumption.
+The concrete ratio depends on the concrete AdaConfigure configuration solutions, such as the solutions listed in Table \ref{tab: different sulutions}.
+For instance, when using the $\beta$ 0.7 solution, the profile time is only 0.2\% of overall resource consumption on this solution; when using the $\beta$ 0.2 solution, the profile cost is 1.5\%.
 
@@
 %	\caption{The effect of different models, frame rate, and resolutions on accuracy and processing time.
-AutoConfigure (blue) consistently outperforms the baseline of one-time update (magenta) across different datasets.
+AdaConfigure (blue) consistently outperforms the baseline of one-time update (magenta) across different datasets.
 Each dot represents the results of running each solution.}

### 2020-12-10 paper/sections/introduction.tex
minor evaluation

@@
 Similarly, specifying a fixed static cheap (e.g., low resolution and small model) configuration will significantly reduce accuracy.
-To tackle these challenges, we propose an adaptive configuration approach, AdaConfigure, and the brief framework is shown in Figure~\ref{fig: framework}(b).
-In our solution, we tackle the following design challenges.
+The brief framework of our solution %To tackle these challenges, we propose an adaptive configuration approach, AdaConfigure, and the brief framework
+is shown in Figure~\ref{fig: framework}(b). In this, we tackle the following design challenges.
 
@@
 For instance, cameras in downtown areas show more cars than the other cameras deployed in the suburbs.
-It is hard to make an exact rule to choose a configuration for the current context by profiling such complicated video's characteristics.
+It is hard to make an exact rule to choose a configuration for the current context by profiling such complicated video characteristics.
 	%As a dynamic video analytics configuration %solution
@@
 In the evaluation, AdaConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 60-90\% of the resources.
-Our solution proves to be more efficient than static solutions and only creates an overhead of 0.1-1\% to the overall video analytics services.
+Our solution proves to be more efficient than static solutions and only creates an overhead of 0.2-2\% to the overall video analytics services.
 \end{itemize}

### 2020-12-10 paper/sections/relatedwork.tex
minor evaluation

@@
 Using different configuration would lead to extra expensive profiling costs.
-To significantly reduce the cost of profiling, we propose an automatic configuration algorithm.
+To significantly reduce the cost of profiling, we propose an automatic and adaptive configuration algorithm.
 \cite{argerich2019orchestration} leverages tabular Q-learning to adapt configuration, but their agent's states only consider last latency.
@@
 
-Our solution, called AutoConfigure, leverages a reinforcement learning-agent to automatically choose the best configuration periodically, effectively improving the analytic accuracy while providing low-resource consumption.
+Our solution, called AdaConfigure, leverages a reinforcement learning-agent to automatically and adaptively choose the best configuration periodically, effectively improving the analytic accuracy while providing low-resource consumption.
 Furthermore, the extra cost of profiling is low since the agent's choosing time is hugely lower.

### 2020-12-11 paper/sections/design.tex
major experiment

@@
 	%	\vspace{0.2cm}
-	\caption{Applying reinforcement learning to automatic configuration}
+	\caption{Applying reinforcement learning to adaptive configuration}
 	\label{fig: DQN}
@@
 
-Figure~\ref{fig: DQN} summarizes how RL can be applied to the automatic configuration.
+Figure~\ref{fig: DQN} summarizes how RL can be applied to the adaptive configuration.
 Briefly, it is a reinforcement learning-based system to train an agent to choose a proper configuration $ c $ for one video chunk to inference.
@@
 
-To automaticly choose different configuration for video stream, we divides the video into T-second intervals as video chunks, and profiles configurations for each video chunk.
+To adaptively choose different configuration for video stream, we divides the video into T-second intervals as video chunks, and profiles configurations for each video chunk.
 Without loss of generality, we denote the object detection service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input video chunk $ x_i $.
@@
 
-For the cost of the object detection service, we use average GPU processing time per frame as the metric of resource consumption because GPU is the dominant resource for the majority of video processing workloads.
+For the cost of the object detection service, we use average GPU processing time per frame as the metric of resource consumption.
 We also denote the metric of resource consumption as $ \hat{s}_{ic} $ that for an input video chunk $ x_i $ and a given configuration $ c $.
@@
 Therefore we can use the Deep Q-learning Network \cite{DQN} as the RL agent.
-But the naive Deep Q-learning Network can not work well in this task because the state space of reinforcement learning is too large if we directly treat video chunk as the input.
+But the naive Deep Q-learning Network can not work well in this task because the state space of reinforcement learning is too large if we directly treat video chunk as the input, making the RL agent extremely difficult to converge.
+
+%But the naive Deep Q-learning Network can not work well in this task because the state space of reinforcement learning is too large if we directly treat video chunk as the input.
 To preserve enough details, we have to add many layers and nodes to the neural network, making the RL agent extremely difficult to converge.
+
 %because of the following challenges: %% \\
@@
 
-To address this challenges, we extract the top $k_1$ representative images from each chunk as spatial features of video chunk.
+To address this challenges, we leverage FFmpeg \cite{FFmpeg} to extract the top $k_1$ representative images from each chunk as spatial features of video chunk.
 We use a pre-trained small neural network to extract the structural information embeddings $ \{e_1,e_2,...,e_{k_1}\} $ of the images to reduce the input dimension and accelerate the training procedure.

### 2020-12-11 paper/sections/experiment.tex
major experiment

@@
 \label{Section: experiment}
+
+\subsection{Experiment Setup and Configuration Selection}
+\label{subsec: configuration}
+We carry out real-world experiments on the object detection task (basic computer vision services) to verify our solution’s performance.
+We use a desktop PC (Intel Xeon E5-2650 v4 CPU) with four NVIDIA 1080ti graphic card as the server infrastructure, and simulate the environment \cite{trade-offs} with three pretrained object detection models in Tensorflow, which are SSD+ResNet152V1, FasterRCNN+ResNet50V1, FasterRCNN+InceptionResNetV2.
+For each model, two kinds of image resolution, which is $1024\times1024$ and $640\times640$, can be picked up.
+In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}.
+We use FFmpeg \cite{ffmpeg} to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model.
+The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.
+In the service inference, the processing video module uses CPU resources, and the object detection module uses GPU resources.
+In our study, we use GPU processing time as the metric of resource consumption because GPU is the dominant resource for most video processing workloads \cite{jiang2018chameleon}.In the evaluation, the processing video module needs 62s to decode 5 mins video into 9000 frames image (i.e., average CPU processing time per frame is about 0.006s), which is lower than the GPU processing time.
+To reduce the latency of processing video, we use different processes to carry out the processing video module and the object detection module in our experiments.
 
@@
 
-For metric, we use the F1 score as the accuracy and average GPU processing time per frame as the resource consumption, detail described in Section \ref{subsec: formulation}. F1 score
+For metric, we use the F1 score as the accuracy and average GPU processing time per frame as the resource consumption, described in Section \ref{subsec: formulation}. F1 score
 is the harmonic mean of precision and recall, where the precision is true positives divided by the detected objects, and the recall is true positives divided by the ground truth objects.
 We identify true positives using two conditions, an abounding box-based condition (only check the classified label) and a label-based condition (check the classified label and spatial overlap \cite{overlap}), consistent with prior work \cite{jiang2018chameleon,noscope}.
-Both metrics are useful in real video analytics services and used in our experiments.
+Both accuracy metrics are useful in real video analytics services and used in our experiments.
 %, consistent with prior work [24, 32].
@@
 
-\subsection{Configuration Selection}
-\label{subsec: configuration}
-We simulate the environment \cite{trade-offs} with three pretrained object detection models in Tensorflow, which are SSD+ResNet152V1, FasterRCNN+ResNet50V1, FasterRCNN+InceptionResNetV2.
-For each model, two kinds of image resolution, which is $1024\times1024$ and $640\times640$, can be picked up.
-In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}.
-We use FFmpeg \cite{ffmpeg} to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model.
-The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.
-
 \subsection{Experiment Parameters}
@@
 Figure \ref{fig: results} shows that AdaConfigure consistently outperforms the baseline of static configuration (profiling configurations once at the beginning of a video stream) along with resource consumption and two accuracy metrics on different datasets.
-Each magenta dot represents one static configuration solution.
+Each magenta dot represents one static configuration solution (one-time profiling).
 These static configuration solutions include some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\} and so on, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\}, \{SSD+ResNet152V1, 640p, 2fps\}, \{SSD+ResNet152V1, 640p, 5fps\} and so on.
@@
 The detailed discussion about differents AdaConfigure solutions is in Section \ref{subsec: different sulutions}.
+Note that AdaConfigure's resource consumption includes both running the best configuration to get inference results and profiling cost of adaptive configuration, which detailed discussed in \ref{subsec: profile cost}.
 As shown in Figure \ref{fig: results}(a)(d), AdaConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 60-80\% of the resources on the M6 dataset.
@@
 AdaConfigure achieves superior performance on multi-camera inference than single-camera inference.
-Instead of the static solution using fixed configuration on different situations, AdaConfigure can choose a proper configuration for different situations since the exact spatial characteristics of the video contents are different in different locations.
+Instead of the static solution using fixed configuration in different situations, AdaConfigure can choose a proper configuration for different situations since the exact spatial characteristics of the video contents are different in different locations.
 It proves that our solution can pick the proper configuration according to intrusive dynamics of video contexts, including spatial and temporal features.
@@
 \label{subsec: different sulutions}
-In the training phase, when using different balance factors $\beta$ in the reward function, we would obtain different agents (different automatic configuration strategies).
+In the training phase, when using different balance factors $\beta$ in the reward function, we would obtain different agents (different adaptive configuration strategies).
+Each exact $\beta$ solution represents a concrete adaptive configuration strategy, which can adaptively update configuration across time.
 In general, the $\beta$ is bigger, indicating the accuracy is more important relatively, and the agent would choose a more expensive configuration.
@@
 The profile cost, including the resource of extract $k_1$ embeddings and the cost of agent choosing actions.
-In our test, the average time of extract one embedding is 0.02s, and the average time of agent choosing action is 0.0006s, which can be ignored.
+We test the average time on 30 hours video of Multi-Camera Dataset, and conclude that the average time of extract one embedding is 0.02s, and the average time of agent choosing action is 0.0006s, which can be ignored.
 We compute the ratio by dividing profile time into total inference time, which is equals the frame number multiply the average time per frame.

### 2020-12-11 paper/sections/introduction.tex
major experiment

@@
 So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations.
-To significantly reduce the resource cost for adaptive configuration profiling requires one solution that automaticly choose a configuration instead of manually trying using various configurations, which is challengling to previous studies including \cite{wang2020jcab,jiang2018chameleon}, since their approach pay attention to reduce search space algorithm and still try using various configurations to find the best configuration.
+To significantly reduce the resource cost for adaptive configuration profiling requires one solution that automatically chooses a configuration instead of manually trying using various configurations, which is challenging to previous studies including \cite{wang2020jcab,jiang2018chameleon} since their approach pay attention to reduce search space algorithm and still try using various configurations to find the best configuration.
 
@@
 
-To address the above complicated decision-making problem and reduce the huge extra overhead of manually trying using various configurations, we carefully design an adaptive configuration framework based on reinforcement learning, which is an excellent approach to solve this unsupervised complex-environmental problem.
-AutoConfigure can adaptively and automatically select the best configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a very low-cost way.
+To address the complicated decision-making problem and reduce the huge extra overhead of manually trying using various configurations, we carefully design an adaptive configuration framework based on reinforcement learning, which is an excellent approach to solve this unsupervised complex-environmental problem.
+AdaConfigure can adaptively and automatically select the best configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a very low-cost way.
 To the best of our knowledge, we are the first to propose an adaptive video configuration solution that adaptively and automatically chooses a configuration according to the current video context.
@@
 Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to adapt the configuration to the current video context.
-In the state design, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance on the multi-camera situation.
-In the reward desgin, we carefully consider both inference accuracy and computation resources to assess each configuration's impact.
+In the state design, we extract the spatial and temporal features of the video context so that the agent can adaptively update the configuration over time and achieve superior performance in the multi-camera situation.
+In the reward design, we carefully consider both inference accuracy and computation resources to assess each configuration's impact.
 Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents.

### 2020-12-12 paper/sections/introduction.tex
minor fig.1
simplify abstract and introduction

--- 2020-12-10 paper/sections/introduction.tex
@@
 \label{Section: introduction}
-With the increasing demand for continuous video analytics in public safety and transportation, more and more cameras are being deployed to various locations.
+%With the increasing demand for continuous video analytics in public safety and transportation, more and more cameras are being deployed to various locations.
 The video analytics are based on classical computer vision techniques as well as deep convolutional neural networks.
@@
 	\item \emph{Choosing the best configuration is a complicated decision-making problem that is challenging to solve by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space.
-For instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but each condition may vary by hour, minute, even second.
+For instance, tracking vehicles when traffic moves quickly requires a higher frame rate than when traffic moves slowly, but each condition may vary by hour, minute, even second.
 Spatially, the characteristics of video content are different in different locations.
@@
 
-	\item \emph{Adaptive configuration would cause a huge extra overhead.} The number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs \cite{jiang2018chameleon}.
+	\item \emph{Adaptive configuration would cause a huge extra overhead.} %The number of possible configurations grows exponentially, 
+There are thousands of configurations can be combined with just a few knobs \cite{jiang2018chameleon}.
 So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations.
@@
 
-To address the above complicated decision-making problem and reduce the huge extra overhead of manually trying using various configurations, we carefully design an adaptive configuration framework based on reinforcement learning, which is an excellent approach to solve this unsupervised complex-environmental problem.
-AutoConfigure can adaptively and automatically select the best configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a very low-cost way.
-To the best of our knowledge, we are the first to propose an adaptive video configuration solution that adaptively and automatically chooses a configuration according to the current video context.
+%To address the above problems, 
+%To address the above complicated decision-making problem and reduce the huge extra overhead of manually trying using various configurations,
+%We carefully design an adaptive configuration framework based on reinforcement learning, which is an excellent approach to solve this unsupervised complex-environmental problem. 
+In our solution, AutoConfigure can adaptively and automatically select the best configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a low-cost way.
+To the best of our knowledge, we are the first to propose an adaptive video configuration solution for such problems.
+%that adaptively and automatically chooses a configuration according to the current video context. 
 The main contributions of this paper are summarized as follows.
@@
 	\item We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to intrusive dynamics of video contexts.
-Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to adapt the configuration to the current video context.
-In the state design, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance on the multi-camera situation.
-In the reward desgin, we carefully consider both inference accuracy and computation resources to assess each configuration's impact.
+Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to decide the configuration for the current video context.
+For the state, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance in the multi-camera situation.
+For the reward, we carefully consider both inference accuracy and computation resources to assess each configuration's impact.
 Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents.
-In our design, our solution can adaptively update configuration strategy over time, and it adaptive to different location-camera inferences and different accuracy-demand services.
+Our solution can adaptively update configuration strategy over time, and it adaptive to different location-camera inferences and different accuracy-demand services.
 	%	 We design an interactive training environment that can be applied to different video analytics applications.

### 2020-12-12 paper/sections/design.tex
minor design

@@
-\section{Detailed Design}
+\section{Reinforcement Learning-based Adaptive Configuration}
+%\section{Detailed Design}
 \label{Section: design}
@@
 
-Initially, the agent tries different configurations $ c $ to obtain inference results image $ x_c $ from input video chunk $ x $.
+Initially, the agent tries different configurations $ c $ to obtain inference results $\vec{y}_c$ from input video chunk $ x $.
 To obtain object detection results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, the agent uses the choosen configuration $ c $ and the reference configuration $ x_{\rm ref} $.
@@
 
-\subsection{RL Agent Design}
+\subsection{RL Agent Design and Video's Characteristics Extraction}
 
@@
 
-To address this challenges, we leverage FFmpeg \cite{FFmpeg} to extract the top $k_1$ representative images from each chunk as spatial features of video chunk.
-We use a pre-trained small neural network to extract the structural information embeddings $ \{e_1,e_2,...,e_{k_1}\} $ of the images to reduce the input dimension and accelerate the training procedure.
+To address this challenges, we leverage FFmpeg \cite{FFmpeg} to extract the top $k_1$ representative images from each chunk and use a pre-trained small neural network to extract the structural Characteristics embeddings $ \{e_1,e_2,...,e_{k_1}\} $ of the images as temporal features to reduce the input dimension and accelerate the training procedure.
 This is a commonly used strategy in training a deep neural network~\cite{finetunning,finetunning2}.
-In this work, we use the early convolution layers of MobileNetV2~\cite{MobileNetV2} as the image feature extractor $ \mathcal{E}(\cdot) $ for its efficiency in image classification.
+In this work, we use the early convolution layers of MobileNetV2~\cite{MobileNetV2} as the image feature extractor $ \mathcal{E}(\cdot) $ for its efficiency in image recognition.
 To extract the temporal features of video chunk, we obtain $ \{\hat{e}_1,\hat{e}_2,...,\hat{e}_{{k_1}-1}\} $ by each embedding subtracting previous embedding.
@@
 
+%To address this challenges, we leverage FFmpeg \cite{FFmpeg} to extract the top $k_1$ representative images from each chunk as characteristics of video chunk
 \subsection{Reinforcement Learning-based Framework}
@@
 
-In the training phase, the RL agent firstly using an $\epsilon-$greedy method to take some random trials to observe the environment's reaction and decreases the randomness when training afterward.
+In the training phase, the RL agent firstly using an $\epsilon$-greedy method to take some random trials to observe the environment's reaction and decreases the randomness when training afterward.
 In iteration $t$, we input state $s_t $ to neural network $ \phi $.
@@
 The framework stores transition $(s_t, c_t, r_t, s_{t+1})$ in a memory buffer $\mathcal{D}$.
-Especially, the transition $(s_t, c_t, r_t, s_{t+1} )$ is uesd to compute the loss function.
 All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $.

### 2020-12-12 paper/sections/experiment.tex
minor design

@@
 In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}.
-We use FFmpeg \cite{ffmpeg} to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model.
+We use FFmpeg to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model.
 The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.
@@
 
-\subsection{Experiment Results}
-\begin{figure*}[!t]
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/Westbound.pdf}}
-		\centerline{(a) Camera 1 (Bounding box-based)}
-	\end{minipage}
-	\hfill
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/Eastbound.pdf}}
-		\centerline{(b) Camera 2 (Bounding box-based)}
-	\end{minipage}
-	\hfill
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/Rear.pdf}}
-		\centerline{(c) Camera 3 (Bounding box-based)}
-	\end{minipage}		
-	\caption{AdaConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different cameras.}
-	\label{fig: 3dataset results}
-\end{figure*}
-
 We use bounding box-based and label-based metric to evaluate AdaConfigure on M6, Duke, and Multi-Camera Dataset video streams.
@@
 It proves that our solution can pick the proper configuration according to intrusive dynamics of video contexts, including spatial and temporal features.
+
+\subsection{Experiment Results}
+\begin{figure*}[!t]
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/Westbound.pdf}}
+		\centerline{(a) Camera 1 (Bounding box-based)}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/Eastbound.pdf}}
+		\centerline{(b) Camera 2 (Bounding box-based)}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[t]{0.32\linewidth}
+		\centerline{\includegraphics[width=6.5cm]{figures/Rear.pdf}}
+		\centerline{(c) Camera 3 (Bounding box-based)}
+	\end{minipage}		
+	\caption{AdaConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different cameras.}
+	\label{fig: 3dataset results}
+\end{figure*}
 

### 2020-12-12 paper/sections/introduction.tex
minor design

@@
 A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector.
-Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}).
+Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD \cite{liu2016ssd}+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN \cite{ren2015faster_rcnn}+\{ResNet \cite{he2016resnet},InceptionResNet \cite{szegedy2016inception}\}).
 A combination of the knob values is video analytics \emph{configuration}, and the configuration space grows \emph{exponentially} with the number of knobs, and their values \cite{jiang2018chameleon}.

### 2020-12-12 paper/sections/experiment.tex
minor experiments
modify bib and simplify content

@@
 
-Most public sources datasets cannot fully satisfy all configuration choices, for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution.
+Most public sources datasets cannot fully satisfy all configuration choices, they provide only a fraction of the requirements for configuration.
+%for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution.
 In contrast, others can ensure resolution but cannot provide a sufficient frame rate.
-Still, in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to search keywords (e.g., "highway traffic") on Youtube and download videos that meet the resolution and frame rate requirements.
+In recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to search keywords (e.g., "highway traffic") on Youtube and download videos that meet the resolution and frame rate requirements.
 We selected three datasets: M6, Duke, and Multi-Camera Dataset.
 M6 was taken from a traffic camera on the longest motorway in Britain.
-Duke is a video from a fixed camera placed at an intersection, and the traffic flow in the video increases or decreases periodically as the traffic light change.
+Duke is a video from a fixed camera placed at an intersection, and the traffic flow in the video increases or decreases periodically with the traffic light change.
 Since the first two datasets were sourced from a fixed camera, to ensure that AdaConfigure performs better in multi-camera inference, we combine three videos collected from different locations into one video dataset, Multi-Camera Dataset.
@@
 
+\subsection{Experiment Results}
 We use bounding box-based and label-based metric to evaluate AdaConfigure on M6, Duke, and Multi-Camera Dataset video streams.
@@
 
-\subsection{Experiment Results}
 \begin{figure*}[!t]

### 2020-12-12 paper/sections/relatedwork.tex
major experiment
modify bib and simplify content

@@
 Notice these reduce search space algorithm still try using various configurations to find the best configuration.
-Using different configuration would lead to extra expensive profiling costs.
+Using different configurations would lead to extra expensive profiling costs.
 To significantly reduce the cost of profiling, we propose an automatic and adaptive configuration algorithm.
@@
 
-Our solution, called AdaConfigure, leverages a reinforcement learning-agent to automatically and adaptively choose the best configuration periodically, effectively improving the analytic accuracy while providing low-resource consumption.
+%Our solution, called AdaConfigure, leverages a reinforcement learning-agent to automatically and adaptively choose the best configuration periodically, effectively improving the analytic accuracy while providing low-resource consumption.
 Furthermore, the extra cost of profiling is low since the agent's choosing time is hugely lower.
+
+AdaConfigure improves the analytic accuracy while providing low-resource consumption. Furthermore, the extra cost of profiling is low since the agent's choosing time is hugely lower.
 

### 2020-12-13 paper/sections/design.tex
major introduction

@@
 Therefore, we have an accuracy metric $ \mathcal{A}_c $ by comparing $ \vec{y}_{\rm ref} $ and $ \vec{y}_c $.
-In general, we use the F1 score as the accuracy $ \mathcal{A} $, which is the harmonic mean of precision and recall, consistent with prior work~\cite{jiang2018chameleon,kang2017f1_noscope,zhang2017f1_live}.
+In general, we use the F1 score as the accuracy $ \mathcal{A} $, detailed described in Section \ref{subsec: datasets}.
 Besides, to compute the accuracy of a frame that was not sampled by $ c $, we use the location of objects from the previous sampled frame.

### 2020-12-13 paper/sections/experiment.tex
major introduction

@@
 The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.
-In the service inference, the processing video module uses CPU resources, and the object detection module uses GPU resources.
+
+%In the service inference, the processing video module uses CPU resources, and the object detection module uses GPU resources.
 In our study, we use GPU processing time as the metric of resource consumption because GPU is the dominant resource for most video processing workloads \cite{jiang2018chameleon}.In the evaluation, the processing video module needs 62s to decode 5 mins video into 9000 frames image (i.e., average CPU processing time per frame is about 0.006s), which is lower than the GPU processing time.
@@
 In contrast, others can ensure resolution but cannot provide a sufficient frame rate.
-In recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to search keywords (e.g., "highway traffic") on Youtube and download videos that meet the resolution and frame rate requirements.
-We selected three datasets: M6, Duke, and Multi-Camera Dataset.
+%In recent years, most of the driving recorder can provide enough resolution and frame rate, so 
+We try to search keywords (e.g., "highway traffic") on Youtube and download videos that meet the resolution and frame rate requirements.
+We selecte three datasets: M6, Duke, and Multi-Camera Dataset.
 M6 was taken from a traffic camera on the longest motorway in Britain.
 Duke is a video from a fixed camera placed at an intersection, and the traffic flow in the video increases or decreases periodically with the traffic light change.
-Since the first two datasets were sourced from a fixed camera, to ensure that AdaConfigure performs better in multi-camera inference, we combine three videos collected from different locations into one video dataset, Multi-Camera Dataset.
+%Since the first two datasets were sourced from a fixed camera, 
+To ensure that AdaConfigure performs better in multi-camera inference, we combine three videos collected from different locations into one video dataset, Multi-Camera Dataset.
 The exact content of this dataset varies significantly over time and across space.
 
-For metric, we use the F1 score as the accuracy and average GPU processing time per frame as the resource consumption, described in Section \ref{subsec: formulation}. F1 score
-is the harmonic mean of precision and recall, where the precision is true positives divided by the detected objects, and the recall is true positives divided by the ground truth objects.
+For metric, we use the F1 score as the accuracy and average GPU processing time per frame as the resource consumption because GPU is the dominant resource for most video processing workloads \cite{jiang2018chameleon}.
+F1 score is the harmonic mean of precision and recall, where the precision is true positives divided by the detected objects, and the recall is true positives divided by the ground truth objects.
 We identify true positives using two conditions, an abounding box-based condition (only check the classified label) and a label-based condition (check the classified label and spatial overlap \cite{overlap}), consistent with prior work \cite{jiang2018chameleon,noscope}.
 Both accuracy metrics are useful in real video analytics services and used in our experiments.
+
+%described in Section \ref{subsec: formulation}.
 %, consistent with prior work [24, 32].
@@
 
-\begin{figure*}[!t]
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/m6.pdf}}
+%\begin{figure*}[!t]
+%	\begin{minipage}[t]{0.32\linewidth}
+%		\centerline{\includegraphics[width=6.5cm]{figures/m6.pdf}}
+%		\centerline{(a) M6 (Bounding box-based)}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}[t]{0.32\linewidth}
+%		\centerline{\includegraphics[width=6.5cm]{figures/duke.pdf}}
+%		\centerline{(b) Duke (Bounding box-based)}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}[t]{0.32\linewidth}
+%		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
+%		\centerline{(c) Multi-Camera Dataset (Bounding box-based)}
+%	\end{minipage}
+%	\vfill
+%%	\vspace{0.4cm}
+%	\begin{minipage}[t]{0.32\linewidth}
+%		\centerline{\includegraphics[width=6.5cm]{figures/m6_label.pdf}}
+%		\centerline{(d) M6 (label-based)}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}[t]{0.32\linewidth}
+%		\centerline{\includegraphics[width=6.5cm]{figures/duke_label.pdf}}
+%		\centerline{(e) Duke (label-based)}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}[t]{0.32\linewidth}
+%		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear_label.pdf}}
+%		\centerline{(f) Multi-Camera Dataset (label-based)}
+%	\end{minipage}		
+%	\caption{AdaConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different metrics on different datasets.
+Each dot represents the results of running each solution.}
+%	\label{fig: results}
+%\end{figure*}
+
+\begin{figure}[!t]
+	\begin{minipage}[t]{0.47\linewidth}
+	\centerline{\includegraphics[width=5cm]{figures/m6.pdf}}
 	\centerline{(a) M6 (Bounding box-based)}
@@
 	\hfill
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/duke.pdf}}
-		\centerline{(b) Duke (Bounding box-based)}
+	\begin{minipage}[t]{0.47\linewidth}
+	\centerline{\includegraphics[width=5cm]{figures/m6_label.pdf}}
+	\centerline{(b) M6 (label-based)}
+	\end{minipage}
+	\vfill
+	\begin{minipage}[t]{0.47\linewidth}
+	\centerline{\includegraphics[width=5cm]{figures/duke.pdf}}
+	\centerline{(c) Duke (Bounding box-based)}
 	\end{minipage}
 	\hfill
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
-		\centerline{(c) Multi-Camera Dataset (Bounding box-based)}
+	%	\vspace{0.4cm}
+	\begin{minipage}[t]{0.47\linewidth}
+	\centerline{\includegraphics[width=5cm]{figures/duke_label.pdf}}
+	\centerline{(d) Duke (label-based)}
 	\end{minipage}
 	\vfill
-	\vspace{0.4cm}
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/m6_label.pdf}}
-		\centerline{(d) M6 (label-based)}
+	\begin{minipage}[t]{0.47\linewidth}
+	\centerline{\includegraphics[width=5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
+	\centerline{(e) Multi-Camera Dataset }%\\ (Bounding box-based)}
+	\centerline{(Bounding box-based)}
 	\end{minipage}
 	\hfill
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/duke_label.pdf}}
-		\centerline{(e) Duke (label-based)}
-	\end{minipage}
-	\hfill
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear_label.pdf}}
-		\centerline{(f) Multi-Camera Dataset (label-based)}
+	\begin{minipage}[t]{0.47\linewidth}
+	\centerline{\includegraphics[width=5cm]{figures/_Westbound_Eastbound_Rear_label.pdf}}
+	\centerline{(f) Multi-Camera Dataset }% (label-based)}
+	\centerline{(label-based)}
 	\end{minipage}		
@@
 	\label{fig: results}
-\end{figure*}
+\end{figure}
 
 \subsection{Experiment Parameters}
-We apply a deep Q-learning network policy to train the agent.
+%We apply a deep Q-learning network policy to train the agent. 
 In the training procedure, we build up to eight independently identical environments for each data set to speed up the training and decrease the data's dependency.
-The leaning rate is set to 0.001.
-For each dataset, we train the agent 10 epochs and 1000 steps per epoch.
+For each dataset, we train the agent 5 epochs and 600 steps (5 mins) per epoch.
 Some important hyperparameters in our experiments are given in Table ~\ref{tab: parameters}.
+%The leaning rate is set to 0.001.
 
@@
 \subsection{Experiment Results}
-We use bounding box-based and label-based metric to evaluate AdaConfigure on M6, Duke, and Multi-Camera Dataset video streams.
-Figure \ref{fig: results} shows that AdaConfigure consistently outperforms the baseline of static configuration (profiling configurations once at the beginning of a video stream) along with resource consumption and two accuracy metrics on different datasets.
+%We use bounding box-based and label-based metric to evaluate AdaConfigure on M6, Duke, and Multi-Camera Dataset video streams. at the beginning of a video stream \{SSD+ResNet152V1, 640p, 2fps\},
+Figure \ref{fig: results} shows that AdaConfigure consistently outperforms the static configuration baseline (only profiling configurations once) along with resource consumption and two accuracy metrics on different datasets.
 Each magenta dot represents one static configuration solution (one-time profiling).
-These static configuration solutions include some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\} and so on, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\}, \{SSD+ResNet152V1, 640p, 2fps\}, \{SSD+ResNet152V1, 640p, 5fps\} and so on.
+These static configuration solutions include some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\} and so on, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\},  \{SSD+ResNet152V1, 640p, 5fps\} and so on.
 Each blue dot represents one AdaConfigure configuration solution, which is dependent on the balance factor $\beta$ in reward function, presented in Section \ref{subsec: reward}.
@@
 Note that AdaConfigure's resource consumption includes both running the best configuration to get inference results and profiling cost of adaptive configuration, which detailed discussed in \ref{subsec: profile cost}.
-As shown in Figure \ref{fig: results}(a)(d), AdaConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 60-80\% of the resources on the M6 dataset.
-As shown in Figure \ref{fig: results}(b)(e), AdaConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 80-90\% of the resources on a Duke dataset.
-As shown in Figure \ref{fig: results}(c)(f), AdaConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 75-85\% of the resources on Multi-Camera Dataset.
+As shown in Figure \ref{fig: results}(a)(b), AdaConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 60-80\% of the resources on the M6 dataset.
+As shown in Figure \ref{fig: results}(c)(d), AdaConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 80-90\% of the resources on a Duke dataset.
+As shown in Figure \ref{fig: results}(e)(f), AdaConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 75-85\% of the resources on Multi-Camera Dataset.
 In a word, AdaConfigure can improve 10-35\% higher accuracy or save 60-90\% resource consumption.
@@
 
-\begin{figure*}[!t]
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/Westbound.pdf}}
-		\centerline{(a) Camera 1 (Bounding box-based)}
+%\begin{figure*}[!t]
+%	\begin{minipage}[t]{0.32\linewidth}
+%		\centerline{\includegraphics[width=6.5cm]{figures/Westbound.pdf}}
+%		\centerline{(a) Camera 1 (Bounding box-based)}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}[t]{0.32\linewidth}
+%		\centerline{\includegraphics[width=6.5cm]{figures/Eastbound.pdf}}
+%		\centerline{(b) Camera 2 (Bounding box-based)}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}[t]{0.32\linewidth}
+%		\centerline{\includegraphics[width=6.5cm]{figures/Rear.pdf}}
+%		\centerline{(c) Camera 3 (Bounding box-based)}
+%	\end{minipage}		
+%	\caption{AdaConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different cameras.}
+%	\label{fig: 3dataset results}
+%\end{figure*}
+
+\begin{figure}[!t]
+	\begin{minipage}[t]{0.47\linewidth}
+		\centerline{\includegraphics[width=5cm]{figures/Westbound.pdf}}
+		\centerline{(a) Camera 1 }%(Bounding box-based)}
+	\centerline{(Bounding box-based)}
 	\end{minipage}
 	\hfill
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/Eastbound.pdf}}
-		\centerline{(b) Camera 2 (Bounding box-based)}
+	\begin{minipage}[t]{0.47\linewidth}
+		\centerline{\includegraphics[width=5cm]{figures/Eastbound.pdf}}
+		\centerline{(b) Camera 2 }%(Bounding box-based)}
+	\centerline{(Bounding box-based)}
 	\end{minipage}
-	\hfill
-	\begin{minipage}[t]{0.32\linewidth}
-		\centerline{\includegraphics[width=6.5cm]{figures/Rear.pdf}}
-		\centerline{(c) Camera 3 (Bounding box-based)}
+	\vfill
+	\begin{minipage}[t]{\linewidth}
+		\centerline{\includegraphics[width=5cm]{figures/Rear.pdf}}
+		\centerline{(c) Camera 3 }%(Bounding box-based)}
+	\centerline{(Bounding box-based)}
 	\end{minipage}		
@@
 	\label{fig: 3dataset results}
-\end{figure*}
+\end{figure}
 
@@
 In this section, we evaluate this profile cost.
-In the inference phase, we divide the video into $T$-second intervals as video chunks and use AdaConfigure to choose the proper configuration for the first t seconds of the video chunk.
+%In the inference phase, we divide the video into $T$-second intervals as video chunks and use AdaConfigure to choose the proper configuration for the first t seconds of the video chunk.
 It then sticks with the chosen configuration for the rest of the video chunk, i.e., for $T-t$ seconds.

### 2020-12-13 paper/sections/introduction.tex
modify bib and simplify content
major introduction

--- 2020-12-12 paper/sections/introduction.tex
@@
 In recent years, we have also witnessed the emergence of a large number of excellent models for target detection \cite{trade-offs}, such as FasterRCNN \cite{ren2015faster_rcnn}, RFCN \cite{dai2016r_fcn}, Multibox \cite{szegedy2014multibox}, SSD \cite{liu2016ssd} and YOLO \cite{redmon2016yolo}.
-
 %For the collected video, the classical computer vision and deep neural network technology are generally used for video analytics. 
-
 A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector.
-Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}).
-A combination of the knob values is video analytics \emph{configuration}, and the configuration space grows \emph{exponentially} with the number of knobs, and their values \cite{jiang2018chameleon}.
+Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution,  detector model selection and so on.
+A combination of the knob values is video analytics \emph{configuration}, and the configuration space grows \emph{exponentially} with the number of knobs and their values \cite{jiang2018chameleon}.
+%(e.g., SSD \cite{liu2016ssd}+{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN \cite{ren2015faster_rcnn}+\{ResNet \cite{he2016resnet},InceptionResNet \cite{szegedy2016inception}\}).
 
@@
 The \emph{best} configuration for video analysis services often varies in minutes or even seconds \cite{jiang2018chameleon}.
-As shown in figure~\ref{fig: framework}(a), if one just uses a fixed static expensive configuration (e.g.
+As shown in Figure~\ref{fig: framework}(a), if one just uses a fixed static expensive configuration (e.g.
 only profiles the processing pipeline \emph{once} to choose high frame rate and resolution) can be very precise, but it can also be a huge drain on resource consumption.
-Similarly, specifying a fixed static cheap (e.g., low resolution and small model) configuration will significantly reduce accuracy.
-The brief framework of our solution %To tackle these challenges, we propose an adaptive configuration approach, AdaConfigure, and the brief framework
-is shown in Figure~\ref{fig: framework}(b). In this, we tackle the following design challenges.
+Similarly, specifying a fixed static cheap configuration (e.g., low resolution and small model) will significantly reduce accuracy.
+The framework of our solution %To tackle these challenges, we propose an adaptive configuration approach, AdaConfigure, and the brief framework
+is shown in Figure~\ref{fig: framework}(b), and we tackle the following design challenges.
 
@@
 	\begin{minipage}{\linewidth}
-		\centerline{\includegraphics[width=0.8\linewidth]{figures/static_framework.pdf}}
+		\centerline{\includegraphics[width=0.9\linewidth]{figures/static_framework.pdf}}
 		\begin{center}
@@
 	\begin{minipage}{\linewidth}
-		\centerline{\includegraphics[width=0.8\linewidth]{figures/auto_framework.pdf}}
+		\centerline{\includegraphics[width=0.9\linewidth]{figures/auto_framework.pdf}}
 		\vspace{0.2cm}
@@
 \begin{itemize}	
-	\item \emph{Choosing the best configuration is a complicated decision-making problem that is challenging to solve by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space.
-For instance, tracking vehicles when traffic moves quickly requires a higher frame rate than when traffic moves slowly, but each condition may vary by hour, minute, even second.
+	\item \emph{Choosing the best configuration is a complicated decision-making problem that is challenging to be solved by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space.
+For instance, tracking vehicles when traffic moves quickly requires a higher frame rate than when traffic moves slowly.
 Spatially, the characteristics of video content are different in different locations.
@@
 It is hard to make an exact rule to choose a configuration for the current context by profiling such complicated video characteristics.
+%	but each condition may vary by hour, minute, even second.
 	%As a dynamic video analytics configuration %solution
@@
 So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations.
-To significantly reduce the resource cost for adaptive configuration profiling requires one solution that automaticly choose a configuration instead of manually trying using various configurations, which is challengling to previous studies including \cite{wang2020jcab,jiang2018chameleon}, since their approach pay attention to reduce search space algorithm and still try using various configurations to find the best configuration.
+To significantly reduce the resource cost for adaptive configuration profiling requires one solution that automaticly choose a configuration instead of manually trying using various configurations, which is challengling to previous studies including \cite{wang2020jcab,jiang2018chameleon}, since their approaches pay attention to reduce search space algorithm and still try using various configurations to find the best configuration.
 
@@
 \begin{itemize}	
-	\item We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to intrusive dynamics of video contexts.
-Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to decide the configuration for the current video context.
-For the state, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance in the multi-camera situation.
-For the reward, we carefully consider both inference accuracy and computation resources to assess each configuration's impact.
+	\item We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to the characteristics of the video stream.
+For the agent's state, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance in the multi-camera situation.
+
+	\item To reduce profiling cost, we leverage a video segmentation strategy and the extremely short choosing action time of agent.
+In particular, we divide the video into $T$-second intervals as video chunks and use the agent to choose the best configuration for the first t seconds of the video chunk, and then sticks with the chosen configuration for the rest of the video chunk ($T-t$ seconds).
+%to capture the characteristics of the video stream with much-reduced computation cost: profiling a segment uses only 0.2-2\% computation resource as compared to a full video.
+%	Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to decide the configuration for the current video context.
+
+	\item For the agent's reward, we carefully consider both inference accuracy and computation resources to assess each configuration's impact.
 Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents.
 Our solution can adaptively update configuration strategy over time, and it adaptive to different location-camera inferences and different accuracy-demand services.
+
+% 	First, we design a reinforcement learning-based framework in which an agent adaptively chooses the configuration according to the spatial and temporal features of the current video stream.
 	%	 We design an interactive training environment that can be applied to different video analytics applications.
@@
 
-	\item We leverage dividing video strategy and the extremely short choosing action time of agent to reduce profiling cost.
+%	\item We leverage dividing video strategy and the extremely short choosing action time of agent to reduce profiling cost.
 In the evaluation, AdaConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 60-90\% of the resources.
 Our solution proves to be more efficient than static solutions and only creates an overhead of 0.2-2\% to the overall video analytics services.
+
+%	\item Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 60-90% of the computation resource.
 \end{itemize}

### 2020-12-13 paper/sections/relatedwork.tex
major introduction

@@
 %\subsection{Configuration optimization} 
-\subsection{Static configuration optimization}
+\subsection{Static Configuration Optimization}
 Several previous papers have considered optimizing video analytics services by either adjusting the configuration knobs or training specialized NN models.
@@
 VideoEdge \cite{hung2018videoedge} introduces \emph{dominant demand} to identify the best tradeoff between multiple resources and accuracy, and narrows the search space by identifying a ``Pareto ban'' of promising configurations.
-MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints.
+%MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints. 
 Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingests and video query.

### 2020-12-13 paper/sections/design.tex
AdaConfigure

@@
 	\label{fig: DQN}
+	\vspace{-0.5cm}
 \end{figure*}
@@
 We use this $ \vec{y}_{\rm ref} $ as the ground truth label.
-For each video chunk $ x_c $ that uses a configuration $ c $, the output $ \vec{y}_c = M(x_c) $.
+For each video chunk $ x_c $ that uses a configuration $ c $, the output is $ \vec{y}_c = M(x_c) $.
 Therefore, we have an accuracy metric $ \mathcal{A}_c $ by comparing $ \vec{y}_{\rm ref} $ and $ \vec{y}_c $.
-In general, we use the F1 score as the accuracy $ \mathcal{A} $, detailed described in Section \ref{subsec: datasets}.
-Besides, to compute the accuracy of a frame that was not sampled by $ c $, we use the location of objects from the previous sampled frame.
-
-For the cost of the object detection service, we use average GPU processing time per frame as the metric of resource consumption.
+In general, we use the F1 score as the accuracy $ \mathcal{A} $ and average GPU processing time per frame as the metric of resource consumption, detailed described in Section \ref{subsec: datasets}.
 We also denote the metric of resource consumption as $ \hat{s}_{ic} $ that for an input video chunk $ x_i $ and a given configuration $ c $.
@@
 
-To address this challenges, we leverage FFmpeg \cite{FFmpeg} to extract the top $k_1$ representative images from each chunk and use a pre-trained small neural network to extract the structural Characteristics embeddings $ \{e_1,e_2,...,e_{k_1}\} $ of the images as temporal features to reduce the input dimension and accelerate the training procedure.
+To address this challenges, we leverage FFmpeg \cite{FFmpeg} to extract the top $k_1$ representative images from each chunk and use a pre-trained small neural network to extract the structural characteristics embeddings $ \{e_1,e_2,...,e_{k_1}\} $ of the images as temporal features to reduce the input dimension and accelerate the training procedure.
 This is a commonly used strategy in training a deep neural network~\cite{finetunning,finetunning2}.
@@
 Besides, we record the last $k_2$ configurations $ \{c_1,c_2,...,c_{k_2}\} $.
-To Solve that vectors of different lengths are not conducive to input to the neural network, we use fully connected layer to transform the spatial embedding $ \{e_1,e_2,...,e_{k_1}\} $, temporal embedding $ \{\hat{e}_1,\hat{e}_2,...,\hat{e}_{{k_1}-1}\} $, and recent configuration $ \{c_1,c_2,...,c_{k_2}\} $ to the fixed length vector, similar to the work~\cite{pensieve}.
+To solve that vectors of different lengths are not conducive to input to the neural network, we use the fully connected layer to transform the spatial embedding $ \{e_1,e_2,...,e_{k_1}\} $, temporal embedding $ \{\hat{e}_1,\hat{e}_2,...,\hat{e}_{{k_1}-1}\} $, and recent configuration $ \{c_1,c_2,...,c_{k_2}\} $ to the fixed length vector, similar to the work~\cite{pensieve}.
 We formulate the fixed length vector $ s $ as \emph{states} and the configuration $ c $ as discrete \emph{actions}.
@@
 
-In our system, we define 48 discrete actions to indicate 48 configuration, and the specific configurations are provided in Section~\ref{subsec: configuration}.
+In our system, we define $k_3$ discrete actions to indicate $k_3$ configuration, and the specific configurations are provided in Section~\ref{subsec: configuration}.
 We denote the \emph{action-value function} as $ Q(s, c; \theta) $ and the optimal compression quality level at time $ t $ as $  c_t = {\rm argmax}_cQ(s, c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.
@@
 
-In the training phase, the RL agent firstly using an $\epsilon$-greedy method to take some random trials to observe the environment's reaction and decreases the randomness when training afterward.
+In the training phase, the RL agent firstly uses a $\epsilon$-greedy method to take some random trials to observe the environment's reaction and decreases the randomness when training afterward.
 In iteration $t$, we input state $s_t $ to neural network $ \phi $.
@@
 
+\setlength{\textfloatsep}{0.1cm}
 \begin{algorithm}[!t]
+%		\setstretch{1.35}
 		\caption{Training RL agent $ \phi $} %in environment $ \{\mathcal{X}, M\} $}
@@
 \end{algorithm}
+\setlength{\floatsep}{0.1cm}
 
@@
 Therefore the overall reward $ r $ should be positively correlated with the accuracy $ \mathcal{A} $ while negatively with the resource consumption ratio $ \Delta s $.
-We introduce a balance factor $ \beta $ to form a linear combination $ r = \beta \mathcal{A} - (1-\beta) \Delta s  $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $.
+We introduce a balance factor $ \beta $ to form a linear combination $ r = \beta \mathcal{A} - (1-\beta) \Delta s  $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $ so that the configuration achieves good accuracy and resource consumption tradeoff.
 %% \\

### 2020-12-13 paper/sections/experiment.tex
AdaConfigure

@@
 The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.
-
 %In the service inference, the processing video module uses CPU resources, and the object detection module uses GPU resources.
@@
 \label{subsec: datasets}
-
 Most public sources datasets cannot fully satisfy all configuration choices, they provide only a fraction of the requirements for configuration.
@@
 %In recent years, most of the driving recorder can provide enough resolution and frame rate, so 
-We try to search keywords (e.g., "highway traffic") on Youtube and download videos that meet the resolution and frame rate requirements.
+We try to search keywords (e.g., ``highway traffic'') on Youtube and download videos that meet the resolution and frame rate requirements.
 We selecte three datasets: M6, Duke, and Multi-Camera Dataset.
-M6 was taken from a traffic camera on the longest motorway in Britain.
+M6 is taken from a traffic camera on the longest motorway in Britain.
 Duke is a video from a fixed camera placed at an intersection, and the traffic flow in the video increases or decreases periodically with the traffic light change.
@@
 Both accuracy metrics are useful in real video analytics services and used in our experiments.
-
+Besides, to compute the accuracy of a frame that is not sampled by exact configuration, we use the location of objects from the previous sampled frame.
 %described in Section \ref{subsec: formulation}.
@@
 	\label{fig: results}
+%	\vspace{-0.5cm} 
 \end{figure}
@@
 	\centering
-	\label{tab: parameters}
 	%     \begin{tabular}{llllll}
@@
 			$ t(inference)  $  &  1   & & &   $ T (inference)  $  &  4      \\ 
+			\bottomrule
 	\end{tabular}}
-	\caption{Experiment parameter}
+	\caption{Experiment parameters}
 	\label{tab: parameters}
@@
 Each magenta dot represents one static configuration solution (one-time profiling).
-These static configuration solutions include some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\} and so on, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\},  \{SSD+ResNet152V1, 640p, 5fps\} and so on.
+These static configuration solutions include some fixed expensive configurations and fixed cheap configurations. 
+%These static configuration solutions include some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\}, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\}, \{SSD+ResNet152V1, 640p, 5fps\}.
 Each blue dot represents one AdaConfigure configuration solution, which is dependent on the balance factor $\beta$ in reward function, presented in Section \ref{subsec: reward}.
-The detailed discussion about differents AdaConfigure solutions is in Section \ref{subsec: different sulutions}.
-Note that AdaConfigure's resource consumption includes both running the best configuration to get inference results and profiling cost of adaptive configuration, which detailed discussed in \ref{subsec: profile cost}.
-As shown in Figure \ref{fig: results}(a)(b), AdaConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 60-80\% of the resources on the M6 dataset.
-As shown in Figure \ref{fig: results}(c)(d), AdaConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 80-90\% of the resources on a Duke dataset.
-As shown in Figure \ref{fig: results}(e)(f), AdaConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 75-85\% of the resources on Multi-Camera Dataset.
+The detailed discussion about different AdaConfigure solutions is in Section \ref{subsec: different sulutions}.
+Note that AdaConfigure's resource consumption includes both running the best configuration to get inference results and profiling cost of adaptive configuration, which detailed discussed in \ref{subsec: profiling cost}.
+
+As shown in Figure \ref{fig: results}, Adaconfigure achieves a high accuracy of 10-35\% with the same amount of computing resources, which benefits from the adaptive selection of relatively expensive configuration when the video content is complex (e.g., traffic congestion, high-speed vehicles).
+Also, Adaconfigure achieves a 50-90\% reduction in resource consumption while achieving almost the same precision as the baseline, which benefits from the adaptive selection of relatively cheap configurations when the video content is simple (e.g., low-traffic flow).
+
+%As shown in Figure \ref{fig: results}, Adaconfigure achieves a high accuracy of 10-35\% with a similar amount of computing resources or achieves a 50-90\% reduction in resource consumption while achieving almost the same precision as the baseline.
+
+%As shown in Figure \ref{fig: results}, (1) Adaconfigure achieves a high accuracy of 10-35\% with the same amount of computing resources, indicating that it can benefit resource constrained settings (for example, edge or mobile devices).
+(2) Adaconfigure achieves a 50-90\% reduction in resource consumption while achieving almost the same precision as the baseline, saving capital costs when resources are resilient but expensive (for example, cloud virtual machines).
+
+%As shown in Figure \ref{fig: results}, there are similar results in different datasets.
+
+%As shown in Figure \ref{fig: results}(a)(b), AdaConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 20-40\% of the resources on the M6 dataset.
+As shown in Figure \ref{fig: results}(c)(d), AdaConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 10-20\% of the resources on a Duke dataset.
+As shown in Figure \ref{fig: results}(e)(f), AdaConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 15-25\% of the resources on Multi-Camera Dataset.
 In a word, AdaConfigure can improve 10-35\% higher accuracy or save 60-90\% resource consumption.
 
-\subsubsection{Superior Performance on Multi-camera Situation}
-\label{subsec: superior performance}
+%\subsubsection{Superior Performance on Multi-camera Situation}
+%\label{subsec: superior performance}
+%
+%\begin{figure}[!t]
+%	\begin{minipage}[t]{0.47\linewidth}
+%		\centerline{\includegraphics[width=5cm]{figures/Westbound.pdf}}
+%		\centerline{(a) Camera 1 }%(Bounding box-based)}
+%		\centerline{(Bounding box-based)}
+%	\end{minipage}
+%	\hfill
+%	\begin{minipage}[t]{0.47\linewidth}
+%		\centerline{\includegraphics[width=5cm]{figures/Eastbound.pdf}}
+%		\centerline{(b) Camera 2 }%(Bounding box-based)}
+%		\centerline{(Bounding box-based)}
+%	\end{minipage}
+%	\vfill
+%	\begin{minipage}[t]{\linewidth}
+%		\centerline{\includegraphics[width=5cm]{figures/Rear.pdf}}
+%		\centerline{(c) Camera 3 }%(Bounding box-based)}
+%		\centerline{(Bounding box-based)}
+%	\end{minipage}		
+%	\caption{AdaConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different cameras.}
+%	\label{fig: 3dataset results}
+%	%	\vspace{-0.5cm}
+%\end{figure}
+%
+%To compare AdaConfigure's performance on single-camera inference and multi-camera inference, we respectively train and test the agent on each single-camera dataset of Multi-Camera Dataset.
+Figure \ref{fig: 3dataset results}(a)(b)(c) shows that AdaConfigure achieves 10-20\% higher accuracy with a similar amount of computation resources.
+%%or achieves similar accuracy with only 50-60\% of the computation resource on the single-camera inference. 
+%As shown in Figure \ref{fig: results}(e), the gap between AdaConfigure and static configuration is larger than Figure \ref{fig: 3dataset results}(a)(b)(c), indicating that AdaConfigure has a better improvement on the multi-camera situation.
+AdaConfigure achieves 25-35\% higher accuracy with a similar amount of resources.
+%%or reach higher accuracy with only 75-85\% of the resources on multi-camera inference.
+%AdaConfigure achieves superior performance on multi-camera inference than single-camera inference.
+Instead of the static solution using fixed configuration in different situations, AdaConfigure can choose a proper configuration for different situations since the exact spatial characteristics of the video contents are different in different locations.
 
-To compare AdaConfigure's performance on single-camera inference and multi-camera inference, we respectively train and test the agent on each single-camera dataset of Multi-Camera Dataset.
-Figure \ref{fig: 3dataset results}(a)(b)(c) shows that AdaConfigure achieves 10-20\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 50-60\% of the resources on a single-camera inference.
-As shown in Figure \ref{fig: results}(c), the gap between AdaConfigure and static configuration is larger than Figure \ref{fig: 3dataset results}(a)(b)(c), indicating that AdaConfigure has a better improvement on the multi-camera situation.
-AdaConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or reach higher accuracy with only 75-85\% of the resources on multi-camera inference.
-AdaConfigure achieves superior performance on multi-camera inference than single-camera inference.
-Instead of the static solution using fixed configuration in different situations, AdaConfigure can choose a proper configuration for different situations since the exact spatial characteristics of the video contents are different in different locations.
-It proves that our solution can pick the proper configuration according to intrusive dynamics of video contexts, including spatial and temporal features.
+%It proves that our solution can pick the proper configuration according to intrusive dynamics of video contexts, including spatial and temporal features.
 
@@
 
-\begin{figure}[!t]
-	\begin{minipage}[t]{0.47\linewidth}
-		\centerline{\includegraphics[width=5cm]{figures/Westbound.pdf}}
-		\centerline{(a) Camera 1 }%(Bounding box-based)}
-	\centerline{(Bounding box-based)}
-	\end{minipage}
-	\hfill
-	\begin{minipage}[t]{0.47\linewidth}
-		\centerline{\includegraphics[width=5cm]{figures/Eastbound.pdf}}
-		\centerline{(b) Camera 2 }%(Bounding box-based)}
-	\centerline{(Bounding box-based)}
-	\end{minipage}
-	\vfill
-	\begin{minipage}[t]{\linewidth}
-		\centerline{\includegraphics[width=5cm]{figures/Rear.pdf}}
-		\centerline{(c) Camera 3 }%(Bounding box-based)}
-	\centerline{(Bounding box-based)}
-	\end{minipage}		
-	\caption{AdaConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different cameras.}
-	\label{fig: 3dataset results}
-\end{figure}
+%\noindnet
+
+\subsubsection{Low Profiling Cost of Adaptive Configuration}
+\label{subsec: profiling cost}
+%Comparing to the static solution that profiles configurations once, in our solution, the video
+%chunk is passed to the AdaConfigure firstly to estimate the configuration. Running this RL agent brings profiling cost (extra resource consumption) to the whole system. 
+%In this section, we evaluate this profiling cost. 
+%In the inference phase, we divide the video into $T$-second intervals as video chunks and use AdaConfigure to choose the proper configuration for the first t seconds of the video chunk.
+It then sticks with the chosen configuration for the rest of the video chunk, i.e., for $T-t$ seconds.
+We use T = 4 and t = 1 for our experiments.
+In our solution, the video chunk is passed to the AdaConfigure firstly to estimate the configuration, bringing profiling cost (extra resource consumption) to the whole system. 
+The profiling cost, including the resource of extract $k_1$ embeddings and the cost of agent choosing actions.
+We test the average time on 30 hours video of Multi-Camera Dataset, and conclude that the average time of extract one embedding is 0.02s, and the average time of agent choosing action is 0.0006s, which can be ignored.
+We compute the ratio by dividing profiling time into total inference time as metric of profiling cost.
+%, which is equals the frame number multiply the average time per frame. 
+The profiling cost is about 0.2-2\% of the overall video analytics resource consumption.
+The concrete ratio depends on the concrete AdaConfigure configuration solutions, such as the solutions listed in Table \ref{tab: different sulutions}.
+For instance, when using the $\beta$ 0.7 solution, the profiling time is only 0.2\% of overall resource consumption on this solution; when using the $\beta$ 0.2 solution, the profiling cost is 1.5\%.
 
@@
 In the training phase, when using different balance factors $\beta$ in the reward function, we would obtain different agents (different adaptive configuration strategies). 
-Each exact $\beta$ solution represents a concrete adaptive configuration strategy, which can adaptively update configuration across time.
+%Each exact $\beta$ solution represents a concrete adaptive configuration strategy, which can adaptively update configuration across time. 
 In general, the $\beta$ is bigger, indicating the accuracy is more important relatively, and the agent would choose a more expensive configuration.
@@
 	\end{tabular}}
-	\caption{Resource consumption and F1 accuracy for different AdaConfigure solutions}
+	\caption{Resource consumption and bounding box-based F1 for different AdaConfigure solutions}
 	\label{tab: different sulutions}
-	% \vspace{-0.5cm}
+	%	\vspace{-0.1cm}
 \end{table}
@@
 We can leverage this to train proper configuration strategy for different service demands, for example, using big $\beta$ for high-accuracy demand services and using small $\beta$ for low-accuracy demand services.
-
-\subsubsection{Low Profiling Cost of Adaptive Configuration}
-\label{subsec: profile cost}
-Comparing to the static solution that profiles configurations once, in our solution, the video
-chunk is passed to the AdaConfigure firstly to estimate the configuration.
-Running this RL agent brings profile cost (extra resource consumption) to the whole system.
-In this section, we evaluate this profile cost.
-%In the inference phase, we divide the video into $T$-second intervals as video chunks and use AdaConfigure to choose the proper configuration for the first t seconds of the video chunk.
-It then sticks with the chosen configuration for the rest of the video chunk, i.e., for $T-t$ seconds.
-We use T = 4 and t = 1 for our experiments.
-The profile cost, including the resource of extract $k_1$ embeddings and the cost of agent choosing actions.
-We test the average time on 30 hours video of Multi-Camera Dataset, and conclude that the average time of extract one embedding is 0.02s, and the average time of agent choosing action is 0.0006s, which can be ignored.
-We compute the ratio by dividing profile time into total inference time, which is equals the frame number multiply the average time per frame.
-The profile cost is about 0.2-2\% of the overall video analytics resource consumption.
-The concrete ratio depends on the concrete AdaConfigure configuration solutions, such as the solutions listed in Table \ref{tab: different sulutions}.
-For instance, when using the $\beta$ 0.7 solution, the profile time is only 0.2\% of overall resource consumption on this solution; when using the $\beta$ 0.2 solution, the profile cost is 1.5\%.
-
 %\begin{table}[!t]

### 2020-12-13 paper/sections/introduction.tex
AdaConfigure

@@
 The \emph{best} configuration for video analysis services often varies in minutes or even seconds \cite{jiang2018chameleon}.
-As shown in Figure~\ref{fig: framework}(a), if one just uses a fixed static expensive configuration (e.g.
-only profiles the processing pipeline \emph{once} to choose high frame rate and resolution) can be very precise, but it can also be a huge drain on resource consumption.
+As shown in Figure~\ref{fig: framework}(a), if one just uses a fixed static expensive configuration (e.g., only profiles the processing pipeline \emph{once} to choose high frame rate and resolution) can be very precise, but it can also be a huge drain on resource consumption.
 Similarly, specifying a fixed static cheap configuration (e.g., low resolution and small model) will significantly reduce accuracy.
@@
 	\label{fig: framework}
+	\vspace{-0.5cm}
 \end{figure*}
 
+\setlist{nolistsep}
 \begin{itemize}	
@@
 So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations.
-To significantly reduce the resource cost for adaptive configuration profiling requires one solution that automaticly choose a configuration instead of manually trying using various configurations, which is challengling to previous studies including \cite{wang2020jcab,jiang2018chameleon}, since their approaches pay attention to reduce search space algorithm and still try using various configurations to find the best configuration.
+To significantly reduce the resource cost for adaptive configuration requires one solution that automatically choose a configuration instead of manually trying using various configurations, which is challengling to previous studies including \cite{jiang2018chameleon,wang2020jcab}, since their approaches pay attention to reduce search space algorithm and still try using various configurations to find the best configuration.
 
@@
 \end{itemize}
-
+\setlist{nolistsep}
 %To address the above problems, 
@@
 %We carefully design an adaptive configuration framework based on reinforcement learning, which is an excellent approach to solve this unsupervised complex-environmental problem. 
-In our solution, AutoConfigure can adaptively and automatically select the best configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a low-cost way.
+In our solution, AdaConfigure can adaptively and automatically select the best configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a low-cost way.
 To the best of our knowledge, we are the first to propose an adaptive video configuration solution for such problems.
@@
 For the agent's state, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance in the multi-camera situation.
-
-	\item To reduce profiling cost, we leverage a video segmentation strategy and the extremely short choosing action time of agent.
-In particular, we divide the video into $T$-second intervals as video chunks and use the agent to choose the best configuration for the first t seconds of the video chunk, and then sticks with the chosen configuration for the rest of the video chunk ($T-t$ seconds).
+	\item We leverage a video segmentation strategy and agent's automatic selection characteristic to reduce profiling cost.
+In particular, we divide the video into $T$-second intervals as video chunks and use the agent to choose the best configuration for the first t seconds of the video chunk.
+It then sticks with the chosen configuration for the rest of the video chunk ($T-t$ seconds).
 %to capture the characteristics of the video stream with much-reduced computation cost: profiling a segment uses only 0.2-2\% computation resource as compared to a full video.
 %	Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to decide the configuration for the current video context.
-
-	\item For the agent's reward, we carefully consider both inference accuracy and computation resources to assess each configuration's impact.
+%the extremely short choosing action time of agent
+	\item We design a reward function that carefully considers both inference accuracy and computation resources to assess each configuration's impact.
 Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents.
-Our solution can adaptively update configuration strategy over time, and it adaptive to different location-camera inferences and different accuracy-demand services.
-
+Our solution can adaptively update configuration strategy over time, and it is adaptive to different location-camera inferences and different accuracy-demand services.
 % 	First, we design a reinforcement learning-based framework in which an agent adaptively chooses the configuration according to the spatial and temporal features of the current video stream.

### 2020-12-13 paper/sections/relatedwork.tex
AdaConfigure

@@
 
-\subsection{Dynamic configuration optimization}
-Some classic works study dynamic optimization problems.
+\subsection{Dynamic Configuration Optimization}
+%Some classic works study dynamic optimization problems.
 INFaaS \cite{romero2019infaas} automatically selects a model, hardware architecture, and any compiler optimizations and makes scaling and resource allocation decisions when application load varies and the available resources vary over time.
@@
 JCAB \cite{wang2020jcab} jointly optimizes configuration adaption, and bandwidth allocation to address several critical challenges in edge-based video analytics systems, including edge capacity limitation, unknown network variation, intrusive dynamics of video contexts.
-Chameleon \cite{jiang2018chameleon} leverages temporal and spatial correlation to amortizes the cost of profiling over time and across multiple cameras and exploit the knob independence to reduce the search space from exponential to linear.
-Notice these reduce search space algorithm still try using various configurations to find the best configuration.
-Using different configurations would lead to extra expensive profiling costs.
+Chameleon \cite{jiang2018chameleon} leverages temporal and spatial correlation to decrease the cost of profiling over time, and exploits the knob independence to reduce the search space from exponential to linear.
+Notice these reduce search space algorithms still try using various configurations to find the best configuration.
+Using different configurations lead to extra expensive profiling costs.
 To significantly reduce the cost of profiling, we propose an automatic and adaptive configuration algorithm.
-\cite{argerich2019orchestration} leverages tabular Q-learning to adapt configuration, but their agent's states only consider last latency.
-Our framework pays attention to the complex and changeable video stream contexts and picks the best configuration according to the current video context.
+\cite{argerich2019orchestration} leverages tabular Q-learning to adapt configuration, but their agent's states only consider inference latency.
+Our framework pays attention to the characteristics of the video stream and picks the best configuration according to the spatial and temporal features of the current video stream.
 
@@
 
-AdaConfigure improves the analytic accuracy while providing low-resource consumption. Furthermore, the extra cost of profiling is low since the agent's choosing time is hugely lower.
+%AdaConfigure improves the analytic accuracy while providing low-resource consumption. Furthermore, the extra cost of profiling is low since the agent's choosing time is hugely lower.
 

### 2020-12-14 paper/sections/experiment.tex
major abstract

@@
 
-\subsection{Experiment Setup and Configuration Selection}
+\subsection{Experiment Setup}
 \label{subsec: configuration}
@@
 
-\subsection{Dataset and Metric}
+\subsection{Datasets and Metric}
 \label{subsec: datasets}
@@
 	%     \begin{tabular}{llllll}
-	\resizebox{0.4\textwidth}{!}{
+	\resizebox{0.45\textwidth}{!}{
 		\begin{tabular}{cccccc}
@@
 The concrete ratio depends on the concrete AdaConfigure configuration solutions, such as the solutions listed in Table \ref{tab: different sulutions}.
-For instance, when using the $\beta$ 0.7 solution, the profiling time is only 0.2\% of overall resource consumption on this solution; when using the $\beta$ 0.2 solution, the profiling cost is 1.5\%.
+For instance, when using the $\beta$ 0.7 solution, the profiling cost is only 0.2\% of overall resource consumption on this solution; when using the $\beta$ 0.2 solution, the profiling cost is 1.5\%.
 
@@
 	%     \begin{tabular}{lll}
-	\resizebox{0.4\textwidth}{!}{
+	\resizebox{0.45\textwidth}{!}{
 		\begin{tabular}{ccc}

### 2020-12-14 paper/sections/introduction.tex
major abstract

@@
 The \emph{best} configuration for video analysis services often varies in minutes or even seconds \cite{jiang2018chameleon}.
-As shown in Figure~\ref{fig: framework}(a), if one just uses a fixed static expensive configuration (e.g., only profiles the processing pipeline \emph{once} to choose high frame rate and resolution) can be very precise, but it can also be a huge drain on resource consumption.
-Similarly, specifying a fixed static cheap configuration (e.g., low resolution and small model) will significantly reduce accuracy.
+As shown in Figure~\ref{fig: framework}(a), if one uses an expensive static configuration (e.g., only profiles the processing pipeline \emph{once} to choose the high frame rate and image resolution) can be precise, but it can also be a huge drain on resource consumption.
+Similarly, specifying a cheap static configuration (e.g., low resolution and small model) will significantly reduce accuracy.
 The framework of our solution %To tackle these challenges, we propose an adaptive configuration approach, AdaConfigure, and the brief framework
@@
 	%\vspace{0.1cm}
-	\caption{Comparing to the static solution, our solution can adaptively update the configuration strategy based on the object detection model feedback}
+	\caption{Comparing to the static solution, our solution can adaptively update the configuration strategy based on the reward feedback}
 	%	\caption{Comparing to the static solution, our solution can update the configuration strategy based on the object detection model feedback}
@@
 
-\setlist{nolistsep}
-\begin{itemize}	
-	\item \emph{Choosing the best configuration is a complicated decision-making problem that is challenging to be solved by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space.
+\emph{Choosing the best configuration is a complicated decision-making problem that is challenging to be solved by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space.
 For instance, tracking vehicles when traffic moves quickly requires a higher frame rate than when traffic moves slowly.
@@
 %As a dynamic video analytics configuration %solution
-	%application, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
+%application, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video context, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
 
-	\item \emph{Adaptive configuration would cause a huge extra overhead.} %The number of possible configurations grows exponentially, 
-	There are thousands of configurations can be combined with just a few knobs \cite{jiang2018chameleon}.
+\emph{Adaptive configuration would cause a huge extra overhead.} The number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs \cite{jiang2018chameleon}.
+So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations.
+To significantly reduce the resource cost for adaptive configuration requires one solution that automatically chooses a configuration instead of manually trying using various configurations, which is challenging to previous studies including \cite{jiang2018chameleon,wang2020jcab}, since their approaches pay attention to reduce search space algorithm, and try various configurations in search space to find the best configuration.
+%using a brute-force search (i.e., periodically trying various configurations and selecting the one with the best performance)
+
+%\setlist{nolistsep}
+%\begin{itemize}	
+%	\item \emph{Choosing the best configuration is a complicated decision-making problem that is challenging to be solved by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space.
+For instance, tracking vehicles when traffic moves quickly requires a higher frame rate than when traffic moves slowly.
+Spatially, the characteristics of video content are different in different locations.
+For instance, cameras in downtown areas show more cars than the other cameras deployed in the suburbs.
+It is hard to make an exact rule to choose a configuration for the current context by profiling such complicated video characteristics.
+%%	but each condition may vary by hour, minute, even second.
+%	%As a dynamic video analytics configuration %solution
+%	%application, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video context, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
+%	
+%	\item \emph{Adaptive configuration would cause a huge extra overhead.} %The number of possible configurations grows exponentially, 
+%	There are thousands of configurations can be combined with just a few knobs \cite{jiang2018chameleon}.
 So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations.
 To significantly reduce the resource cost for adaptive configuration requires one solution that automatically choose a configuration instead of manually trying using various configurations, which is challengling to previous studies including \cite{jiang2018chameleon,wang2020jcab}, since their approaches pay attention to reduce search space algorithm and still try using various configurations to find the best configuration.
+%	
+%	%We leverage a Reinforcement Learning-based agent to adaptively pick the best configuration periodically, dramatically reducing the profiling cost. 
+%	%How to significantly reduce the resource cost of periodic configuration profiling.
+%	
+%	%\item \emph{Lack of well-labeled training data.} In our case, there was no well-marked data that indicated which configuration should be choosed at which time of the video, as is the case with traditional deep learning tasks.%In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks.
+In practice, such a video analytics configuration is usually utilized online, and the solution has to adaptively learn from the video context.
+%\end{itemize}
+%\setlist{nolistsep}
 
-	%We leverage a Reinforcement Learning-based agent to adaptively pick the best configuration periodically, dramatically reducing the profiling cost. 
-	%How to significantly reduce the resource cost of periodic configuration profiling.
-
-	%\item \emph{Lack of well-labeled training data.} In our case, there was no well-marked data that indicated which configuration should be choosed at which time of the video, as is the case with traditional deep learning tasks.%In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks.
-In practice, such a video analytics configuration is usually utilized online, and the solution has to adaptively learn from the video contexts.
-\end{itemize}
-\setlist{nolistsep}
 %To address the above problems, 
@@
 %We carefully design an adaptive configuration framework based on reinforcement learning, which is an excellent approach to solve this unsupervised complex-environmental problem. 
-In our solution, AdaConfigure can adaptively and automatically select the best configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a low-cost way.
+In our solution, AdaConfigure can adaptively and automatically select the best configuration according to intrusive dynamics of video context, thus solving this difficult optimal configuration decision problem in a low-cost way.
 To the best of our knowledge, we are the first to propose an adaptive video configuration solution for such problems.
@@
 
-\begin{itemize}	
-	\item We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to the characteristics of the video stream.
+We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to the characteristics of the video stream.
 For the agent's state, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance in the multi-camera situation.
-	\item We leverage a video segmentation strategy and agent's automatic selection characteristic to reduce profiling cost.
+
+We leverage  agent's automatic selection characteristic and the video segmentation strategy to reduce profiling cost.
 In particular, we divide the video into $T$-second intervals as video chunks and use the agent to choose the best configuration for the first t seconds of the video chunk.
-It then sticks with the chosen configuration for the rest of the video chunk ($T-t$ seconds).
-%to capture the characteristics of the video stream with much-reduced computation cost: profiling a segment uses only 0.2-2\% computation resource as compared to a full video.
-%	Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to decide the configuration for the current video context.
-%the extremely short choosing action time of agent
-	\item We design a reward function that carefully considers both inference accuracy and computation resources to assess each configuration's impact.
+It then sticks with the chosen configuration for the rest of the video chunk ($T-t$ seconds) to reduce profiling number.
+In the evaluation, the profiling cost is about 0.2-2\% of the overall video analytics resource consumption.
+
+We design a reward function that considers both inference accuracy and computation resources to assess each configuration's impact.
 Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents.
 Our solution can adaptively update configuration strategy over time, and it is adaptive to different location-camera inferences and different accuracy-demand services.
-% 	First, we design a reinforcement learning-based framework in which an agent adaptively chooses the configuration according to the spatial and temporal features of the current video stream.
-	%	 We design an interactive training environment that can be applied to different video analytics applications.
-	%	\item We build a reinforcement learning-based framework to train the agent in the above environment.
+Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 50-90\% of the computation resource.
+
+%\begin{itemize}	
+%	\item We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to the characteristics of the video stream.
+For the agent's state, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance in the multi-camera situation.
+%	\item We leverage  agent's automatic selection characteristic and the video segmentation strategy to reduce profiling cost.
+In particular, we divide the video into $T$-second intervals as video chunks and use the agent to choose the best configuration for the first t seconds of the video chunk.
+It then sticks with the chosen configuration for the rest of the video chunk ($T-t$ seconds) to reduce profiling number.
+In the evaluation, the profiling cost is about 0.2-2\% of the overall video analytics resource consumption.
+%%to capture the characteristics of the video stream with much-reduced computation cost: profiling a segment uses only 0.2-2\% computation resource as compared to a full video.
+%%	Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to decide the configuration for the current video context.
+%%the extremely short choosing action time of agent
+%	\item We design a reward function that considers both inference accuracy and computation resources to assess each configuration's impact.
+Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents.
+Our solution can adaptively update configuration strategy over time, and it is adaptive to different location-camera inferences and different accuracy-demand services.
+Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 50-90\% of the computation resource.
+%% 	First, we design a reinforcement learning-based framework in which an agent adaptively chooses the configuration according to the spatial and temporal features of the current video stream.
+%	%	 We design an interactive training environment that can be applied to different video analytics applications.
+%	%	\item We build a reinforcement learning-based framework to train the agent in the above environment.
 The agent can learn to choose a ``most appropriate'' configuration for each timestamp of video analytics after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and resources.
-
-%	\item We leverage dividing video strategy and the extremely short choosing action time of agent to reduce profiling cost.
+%	
+%%	\item We leverage dividing video strategy and the extremely short choosing action time of agent to reduce profiling cost.
 In the evaluation, AdaConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 60-90\% of the resources.
 Our solution proves to be more efficient than static solutions and only creates an overhead of 0.2-2\% to the overall video analytics services.
-
-%	\item Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 60-90% of the computation resource.
-\end{itemize}
+%	
+%%	\item Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 60-90% of the computation resource.
+%\end{itemize}
 

### 2020-12-14 paper/sections/relatedwork.tex
major abstract

@@
 VideoEdge \cite{hung2018videoedge} introduces \emph{dominant demand} to identify the best tradeoff between multiple resources and accuracy, and narrows the search space by identifying a ``Pareto ban'' of promising configurations.
-%MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints. 
-Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingests and video query.
-By tuning the share of computing resources of both phases, Focus achieves an effective and flexible tradeoff of video analytics's latency and accuracy.
+MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints.
+Focus \cite{hsieh2018focus} deconstructs video analytics into two phases (i.e., video ingests and video query), achieving an effective and flexible tradeoff of video analytics's latency and accuracy.
 These algorithms all profile and optimize video analytics only once at the beginning of the video.
@@
 In other words, they do not handle changes in video stream context.
-But the optimal configurations do change over time because of the complex and changeable video stream contexts.
+But the optimal configurations do change over time because of the complex and changeable video stream context.
+
+%Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingests and video query.
+By tuning the share of computing resources of both phases, Focus achieves an effective and flexible tradeoff of video analytics's latency and accuracy.
 
@@
 Some papers study how to dynamically optimize the configuration for video analytics when the video stream context changes.
-JCAB \cite{wang2020jcab} jointly optimizes configuration adaption, and bandwidth allocation to address several critical challenges in edge-based video analytics systems, including edge capacity limitation, unknown network variation, intrusive dynamics of video contexts.
-Chameleon \cite{jiang2018chameleon} leverages temporal and spatial correlation to decrease the cost of profiling over time, and exploits the knob independence to reduce the search space from exponential to linear.
-Notice these reduce search space algorithms still try using various configurations to find the best configuration.
+JCAB \cite{wang2020jcab} jointly optimizes configuration adaption, and bandwidth allocation to address several critical challenges in edge-based video analytics systems, including edge capacity limitation, unknown network variation, intrusive dynamics of video context.
+Chameleon \cite{jiang2018chameleon} leverages temporal and spatial correlation to decrease the cost of profiling, and exploits the knob independence to reduce the search space from exponential to linear.
+Notice these reduce search space algorithms still trying various configurations to find the best configuration.
 Using different configurations lead to extra expensive profiling costs.

### 2020-12-14 paper/sections/design.tex
major abstract
submit ICME

@@
 	%	\vspace{0.2cm}
-	\caption{Applying reinforcement learning to adaptive configuration}
+	\caption{Applying reinforcement learning to adaptive configuration.}
 	\label{fig: DQN}
@@
 
-\subsection{RL Agent Design and Video's Characteristics Extraction}
+\subsection{RL Agent Design and Video Characteristic Extraction}
 
@@
 The training procedure would converge when the agent's randomness keeps decaying.
-Finally, the agent's action is based on its historical ``optimal'' experiences.
+Finally, the agent's actions are based on its historical ``optimal'' experiences.
 The training procedure is presented in Algorithm~\ref{alg: rl-train}.
@@
 			\STATE Obtain $ (\vec{y}_{\rm ref}, \vec{y}_c) $ from the object detection service
-			\STATE Compute reward $ r \leftarrow R(\Delta s, \mathcal{A}_c) $ according to \ref{subsec: reward} Reward Feedback Design 
+			\STATE Compute reward $ r \leftarrow R(\Delta s, \mathcal{A}_c) $ according to \ref{subsec: reward} Reward Feedback 
 			\STATE \textbf{3) Gradient descent}
@@
 
-\subsection{Reward Feedback Design}
+\subsection{Reward Feedback}
 \label{subsec: reward}

### 2020-12-14 paper/sections/experiment.tex
submit ICME

@@
 In the training procedure, we build up to eight independently identical environments for each data set to speed up the training and decrease the data's dependency.
-For each dataset, we train the agent 5 epochs and 600 steps (5 mins) per epoch.
+For each dataset, we train the agent 5 epochs and 600 steps (5 minutes) per epoch.
 Some important hyperparameters in our experiments are given in Table ~\ref{tab: parameters}.
@@
 	\end{tabular}}
-	\caption{Experiment parameters}
+	\caption{Experiment parameters.}
 	\label{tab: parameters}
@@
 We use T = 4 and t = 1 for our experiments.
+\hyphenation{profiling} 
+\hyphenation{embeddings}
 In our solution, the video chunk is passed to the AdaConfigure firstly to estimate the configuration, bringing profiling cost (extra resource consumption) to the whole system. 
@@
 The concrete ratio depends on the concrete AdaConfigure configuration solutions, such as the solutions listed in Table \ref{tab: different sulutions}.
-For instance, when using the $\beta$ 0.7 solution, the profiling cost is only 0.2\% of overall resource consumption on this solution; when using the $\beta$ 0.2 solution, the profiling cost is 1.5\%.
+For instance, when using the solution of $\beta$=0.7, the profiling cost is only 0.2\% of overall resource consumption on this solution; when using the solution of $\beta$=0.2, the profiling cost is 1.5\%.
 
+%For instance, the profiling cost is only 0.2\% of overall resource consumption on the solution of 0.7 $\beta$; and the profiling cost is 1.5\% on the solution of 0.2 $\beta$.
 \subsubsection{Different AdaConfigure Solutions to Meet Different Services}
@@
 	\end{tabular}}
-	\caption{Resource consumption and bounding box-based F1 for different AdaConfigure solutions}
+	\caption{Resource consumption and bounding box-based F1 for different AdaConfigure solutions.}
 	\label{tab: different sulutions}

### 2020-12-14 paper/sections/introduction.tex
key word
submit ICME

@@
 		\begin{center}
-			{(a) Static configuration solution: fixed configuration for video analytics services}
+			{(a) Static configuration solution: fixed configuration for video analytics services.}
 		\end{center}
@@
 		\begin{center}
-			{(b) AdaConfigure solution: reinforcement learning-based adaptive configuration framework}
+			{(b) AdaConfigure solution: reinforcement learning-based adaptive configuration framework.}
 		\end{center}
@@
 	%\vspace{0.1cm}
-	\caption{Comparing to the static solution, our solution can adaptively update the configuration strategy based on the reward feedback}
+	\caption{Comparing to the static solution, our solution can adaptively update the configuration strategy based on the reward feedback.}
 	%	\caption{Comparing to the static solution, our solution can update the configuration strategy based on the object detection model feedback}
@@
 Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents.
-Our solution can adaptively update configuration strategy over time, and it is adaptive to different location-camera inferences and different accuracy-demand services.
-Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 50-90\% of the computation resource.
+Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 10-50\% of the computation resource.
 
+%Our solution can adaptively update configuration strategy over time, and it is adaptive to different location-camera inferences and different accuracy-demand services.
 %\begin{itemize}	
